### 2025-04-22 ABP_heatmap_for_Cece_20241018.Rmd
Adding R project, scripts to process data and generate figures, and all helper csv's

---
title: "Cece Sed Traps Manuscript Heat Map"
author: "Adrienne Breef-Pilz"
date: "2024-10-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(tidyverse, akima, reshape2, gridExtra, colorRamps, RColorBrewer, ggpubr, geomtextpath, scales)

source("https://raw.githubusercontent.com/CareyLabVT/Reservoirs/master/Data/DataAlreadyUploadedToEDI/EDIProductionFiles/Heatmap_EDI_function.R")
```

```{r Read in files}

# Read in from EDI

 EDI_CTD <-
  read_csv("https://pasta.lternet.edu/package/data/eml/edi/200/14/0432a298a90b2b662f26c46071f66b8a")%>%
  #read_csv("./../../Raw_CTD/ctd_L1.csv")|>
   filter(DateTime>ymd_hms("2018-01-01 00:00:00") & DateTime<ymd_hms("2023-12-31 00:00:00"))%>%
   filter(Reservoir=="BVR"|Reservoir=="FCR")%>%
   filter(Site==50)%>%
   select(-starts_with("Flag"))%>%
  mutate(Year=year(DateTime))%>%
  filter(Depth_m>0)

# Make a df of just the casts

CTD_casts <- EDI_CTD |>
  select(Reservoir, DateTime, Year)|>
  unique()

# GEt the month and date for easier graphing. This is not the correct date.   
  CTD_casts$MDay <- format(CTD_casts$DateTime,"%m-%d")
  CTD_casts$MDay <- as.Date(CTD_casts$MDay, "%m-%d")

```

```{r Turnover}

### Still working on this

source("https://raw.githubusercontent.com/LTREB-reservoirs/vera4cast/refs/heads/main/targets/target_functions/target_generation_mixed_binary_daily.R")

bvr_current <- c("https://raw.githubusercontent.com/FLARE-forecast/BVRE-data/bvre-platform-data-qaqc/bvre-waterquality_L1.csv")
#bvr_current = NULL
bvr_historic <- c("https://pasta.lternet.edu/package/data/eml/edi/725/4/9adadd2a7c2319e54227ab31a161ea12")

a <- target_generation_mixed_binary_daily(bvr_current, bvr_historic)

bvr_turnover <- a|>
  mutate(Year = year(datetime),
         DOY = yday(datetime))|>
  filter(observation==1 & DOY>200)|>
  group_by(Year)|>
  slice_min(datetime, n = 1)

# Get turnover for FCR

fcr_historic <- "https://pasta.lternet.edu/package/data/eml/edi/271/8/fbb8c7a0230f4587f1c6e11417fe9dce"

fcr_current <- "https://raw.githubusercontent.com/FLARE-forecast/FCRE-data/refs/heads/fcre-catwalk-data-qaqc/fcre-waterquality_L1.csv"

ag <- target_generation_mixed_binary_daily(fcr_current, fcr_historic)

fcr_turnover <- ag|>
  mutate(Year = year(datetime),
         DOY = yday(datetime))|>
  filter(observation==1 & DOY>200)|>
  group_by(Year)|>
  slice_min(datetime, n = 1)

## in the dates Cece has here

turnover <- dplyr::bind_rows(fcr_turnover,bvr_turnover)|>
  mutate(Reservoir=ifelse(site_id=="fcre", "FCR", "BVR"))|>
  filter(datetime<as.Date("2024-01-01"))|>
  select(datetime, Reservoir, Year)

# Add in BVR observations
turn <- data.frame(
  datetime = c(as.Date("2018-10-24"), as.Date("2019-11-02")),
  Reservoir = c("BVR", "BVR"),
  Year = c(2018, 2019)
)

turnover <- dplyr::bind_rows(turn, turnover)

# GEt the month and date for easier graphing. This is not the correct date.   
  turnover$MDay <- format(turnover$datetime,"%m-%d")
  turnover$MDay <- as.Date(turnover$MDay, "%m-%d")
```

```{r make heat map df}

# This function makes a data frame of interpolated observations over the years for making multiple heat maps using facet_grid

heat_interp <- function(
    data,
    var,
    Res,
    Years){

  # data= "EDI_CTD_temp"
  # var = "Temp_C"
  # Res = "FCR"
  # Years = 2023

  interp <- data.frame(x = NA, y = NA, z = NA, Reservoir = NA)

 bvr <- get(data) %>%
   select(Reservoir, DateTime, Depth_m, var) |>
        mutate(Year = year(DateTime),
               Date = as.Date(DateTime))%>%
        filter(#Reservoir == "BVR",
               !is.na(get(var)),
               !is.na(Depth_m),
               Reservoir %in% Res,
               Year %in% Years)

      if(nrow(bvr)>0){
        interp <- interp2xyz(interp(x = as.numeric(bvr$Date), y= bvr$Depth_m, z= unlist(bvr[[var]]),
                                        xo = seq(min(bvr$Date), max(bvr$Date), "day"),
                                        yo = seq(min(bvr$Depth_m), max(bvr$Depth_m), 
                                                 by = 0.1), 
                                        duplicate = "mean"),data.frame = T)
        interp2<-interp%>%
    mutate(Date=as.Date(x, origin = "1970-01-01"),
           Reservoir=Res)

  return(interp2)
  }
}
```

```{r plotting}

#custom_heatmap_palettes <- c("#313695", "#4575b4", "#74add1",
#                            "#abd9e9", "#e0f3f8", "#ffffbf", 
#                            "#fee090","#fdae61", "#f46d43", 
#                            "#d73027", "#a50026")

make_heat_map <- function(
    data,
    sample_dates,
    turnovers, 
    y_lim,
    custom_heatmap_palette,
    y_units,
    output_file){

#Heatmap

# change the plots dimensions  
jpeg(paste0(output_file),width = 8, height = 4, units = "in", res = 400)
water_temp <- data%>%
  mutate(x = as.Date(x, origin = "1970-01-01"),
         Year = year(x))%>%
  filter(!is.na(z))%>%
  ggplot()+
  geom_raster(aes(x=MDay, y=y,fill = z))+
  geom_point(data = sample_dates, aes(x = MDay, y = 0.1, z = NULL), pch = '|', size = 2, color = "black") + #to mark cast dates 
   geom_vline(data= turnovers, aes(xintercept=MDay) , linetype="solid", color="black", linewidth=0.5) +
  labs(y = "Depth (m)") +
  scale_x_date(expand = c(0,0)) +
  scale_y_reverse(expand = c(0,0)) +
  #scale_y_continuous(expand = c(0,0))+
  theme(panel.border = element_rect(fill = NA),
        axis.title.x=element_blank())+
  scale_fill_gradientn(name = y_units,
                       limits = y_lim,
                       colours = custom_heatmap_palette)+
  facet_grid(rows= vars(Reservoir),cols = vars(Year),
             scales = "free_y",
             space = "free"
             )+
  theme(panel.background = element_rect(fill = "white"),
          panel.spacing.x = unit(0.05, "lines"),
        legend.position = 'bottom',
        panel.grid = element_blank())
  theme_bw(base_size = 18)
  # labs(color = "")+
  # geom_point(data = sensor_depth_plot, 
  #            aes(x = Date, y = Sensor_depth), 
  #            shape = 23, fill = "black", color = "white", size  =2.5)+
  # geom_vline(data=lines,aes(xintercept = Dates), show.legend = F)+
  # scale_linetype_manual(values = c("solid","84"),
  #                       limits = c("Thermocline","Outtake pipe"),  
  #                       name= NULL)+

print(water_temp)
dev.off()

}
```

```{r Make Temp plot}

# EDI_CTD_temp <- EDI_CTD|>
#   select(Reservoir, DateTime, Year, Depth_m, Temp_C)

wer <- data.frame(
  data= c(rep("EDI_CTD",12)),
  var = c(rep("Temp_C",12)),
  Res = c(rep("FCR",6), rep("BVR",6)),
  Years = c(rep(2018:2023,2))
)

system.time(sd <- wer%>%
             pmap(heat_interp))

#Bind all the QAQC files from above
   temp_df <- dplyr::bind_rows(sd)

  temp_df <- temp_df%>%
    filter(!is.na(Reservoir),
           y>0.1)

# GEt the month and date for easier graphing. This is not the correct date.   
  temp_df$MDay <- format(temp_df$Date,"%m-%d")
temp_df$MDay <- as.Date(temp_df$MDay, "%m-%d")

# make the plot

make_heat_map(
  data= temp_df,
  sample_dates = CTD_casts,
  turnovers = turnover, 
  y_lim = c(-1, 30),
  custom_heatmap_palette = blue2green2red(60),
  y_units = "Water temperature (°C)",
  output_file = "figures/SedTraps_CTD_waterTemp_2018_2023.jpeg"
)

```

```{r Make DO plot}

# EDI_CTD_temp <- EDI_CTD|>
#   select(Reservoir, DateTime, Year, Depth_m, Temp_C)

wer <- data.frame(
  data= c(rep("EDI_CTD",12)),
  var = c(rep("DO_mgL",12)),
  Res = c(rep("FCR",6), rep("BVR",6)),
  Years = c(rep(2018:2023,2))
)

system.time(sd <- wer%>%
             pmap(heat_interp))

#Bind all the QAQC files from above
   temp_df <- dplyr::bind_rows(sd)

  temp_df <- temp_df%>%
    filter(!is.na(Reservoir),
           y>0.1)

# GEt the month and date for easier graphing. This is not the correct date.   
  temp_df$MDay <- format(temp_df$Date,"%m-%d")
temp_df$MDay <- as.Date(temp_df$MDay, "%m-%d")

# make the plot

make_heat_map(
  data= temp_df,
  sample_dates = CTD_casts,
  turnovers = turnover, 
  y_lim = c(-1,16),
  custom_heatmap_palette = rev(blue2green2red(60)),
  y_units = "Dissolved Oxygen mg/L",
  output_file = "figures/SedTraps_CTD_DO_2018_2023.jpeg"
)

```

```{r Need to add in handhelp pH obs}

ph <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/198/12/e0181372c6d4cbc66eca4644f8385470" )|>
  #read_csv("./../../../DataAlreadyUploadedToEDI/EDIProductionFiles/MakeEMLYSI_PAR_secchi/2023/YSI_PAR_profiles_2013_2023.csv")|>
  filter(DateTime>as.Date("2018-01-01"))|>
  filter(Reservoir=="BVR"|Reservoir=="FCR")|>
   filter(Site==50)|>
  select(Reservoir, DateTime, Depth_m, pH)|>
  drop_na(pH)|>
  mutate(Year=year(DateTime))

# bind with the CTD

EDI_CTD_ph <- dplyr::bind_rows(EDI_CTD,ph)

CTD_casts_ph <- ph|>
  select(Reservoir, DateTime, Year)|>
  mutate(DateTime = as.Date(DateTime))|>
  unique()%>%
  dplyr::bind_rows(. , CTD_casts)

# GEt the month and date for easier graphing. This is not the correct date.   
  CTD_casts_ph$MDay <- format(CTD_casts_ph$DateTime,"%m-%d")
  CTD_casts_ph$MDay <- as.Date(CTD_casts_ph$MDay, "%m-%d")
```

```{r Make pH plot}

##Need to fix this

 EDI_CTD_pH <- EDI_CTD|>
   select(Reservoir, DateTime, Year, Depth_m, pH)%>%
  bind_rows(.,ph)

wer <- data.frame(
  data= c(rep("EDI_CTD_pH",12)),
  var = c(rep("pH",12)),
  Res = c(rep("FCR",6), rep("BVR",6)),
  Years = c(rep(2018:2023,2))
)

system.time(sd <- wer%>%
             pmap(heat_interp))

#Bind all the QAQC files from above
   temp_df <- dplyr::bind_rows(sd)

  temp_df <- temp_df%>%
    filter(!is.na(Reservoir),
           y>0.1)

# GEt the month and date for easier graphing. This is not the correct date.   
  temp_df$MDay <- format(temp_df$Date,"%m-%d")
temp_df$MDay <- as.Date(temp_df$MDay, "%m-%d")

# make the plot

make_heat_map(
  data= temp_df,
  sample_dates = CTD_casts_ph,
  turnovers = turnover,
  y_lim = c(5,10),
  custom_heatmap_palette = blue2green2red(60),
  y_units = "pH",
  output_file = "figures/SedTraps_CTD_pH_2018_2023.jpeg"
)

```

```{r metals plotting}

make_metals_heat_map <- function(
    data,
    sample_dates,
    turnovers, 
    y_lim,
    custom_heatmap_palette,
    y_units){

#Heatmap

# change the plots dimensions  
#jpeg(paste0(output_file),width = 8, height = 4, units = "in", res = 400)
water_temp <- data%>%
  mutate(x = as.Date(x, origin = "1970-01-01"),
         Year = year(x))%>%
  filter(!is.na(z))%>%
  ggplot()+
  geom_raster(aes(x=MDay, y=y,fill = z))+
  geom_point(data = sample_dates, aes(x = MDay, y = 0.1, z = NULL), pch = '|', size = 2, color = "gray80") + #to mark cast dates 
   geom_vline(data= turnovers, aes(xintercept=MDay) , linetype="solid", color="gray80", linewidth=0.5) +
  labs(y = "Depth (m)") +
  scale_x_date(expand = c(0,0)) +
  scale_y_reverse(expand = c(0,0),
                  breaks = c(0.0, 2.5, 5.0, 7.5)) +
  #scale_y_continuous(expand = c(0,0))+
  theme(panel.border = element_rect(fill = NA),
        axis.title.x=element_blank()) +
  scale_fill_gradientn(name = y_units,
                       limits = y_lim,
                       colours = custom_heatmap_palette,
                       values=rescale(c(0,5,20)))+
  facet_grid(rows= vars(Reservoir),cols = vars(Year),
             scales = "free_y",
             space = "free"
             )+
  theme(panel.background = element_rect(fill = "white"),
          panel.spacing = unit(0.05, "lines"),
        legend.position = 'bottom',
        panel.grid = element_blank())
  theme_bw(base_size = 18)
  # labs(color = "")+
  # geom_point(data = sensor_depth_plot, 
  #            aes(x = Date, y = Sensor_depth), 
  #            shape = 23, fill = "black", color = "white", size  =2.5)+
  # geom_vline(data=lines,aes(xintercept = Dates), show.legend = F)+
  # scale_linetype_manual(values = c("solid","84"),
  #                       limits = c("Thermocline","Outtake pipe"),  
  #                       name= NULL)+

return(water_temp)
dev.off()

}
```

```{r}
metals <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/455/8/9c8c61b003923f4f03ebfe55cea8bbfd")

# filter the data to the time you want. Right now this is just for 2021.

met <- metals |>
  filter(year(DateTime)>= 2018 & Depth_m <= 9)

met <- met %>% 
  filter(Flag_TFe_mgL != 8 & Flag_SFe_mgL != 8 & Flag_TFe_mgL != 68 & Flag_SFe_mgL != 68,
       Flag_TMn_mgL != 8 & Flag_SMn_mgL != 8 & Flag_TMn_mgL != 68 & Flag_SMn_mgL != 68)

# ratios of S to T for plotting 
met <- met %>% 
  mutate(FeDiff = TFe_mgL - SFe_mgL,
         MnDiff = TMn_mgL - SMn_mgL,
         Year = year(DateTime),
         Date = format(DateTime,"%m-%d"))

#create a data frame with the correct values
metratio <- met %>% 
  filter(FeDiff > 0,
         MnDiff > 0)

#create a data frame with the incorrect values and switch them
met_issues <- met %>% 
  filter(FeDiff < 0,
         MnDiff < 0) %>% 
  rename('test1' = 'TMn_mgL',
         'test2' = 'SMn_mgL',
         'testA' = 'TFe_mgL',
         'testB' = 'SFe_mgL') %>% 
  rename('TMn_mgL' = 'test2',
         'SMn_mgL' = 'test1',
         'TFe_mgL' = 'testB',
         'SFe_mgL' = 'testA') %>% 
  mutate(MnDiff = TMn_mgL - SMn_mgL,
         FeDiff = TFe_mgL - SFe_mgL)

#rbind to rejoin
metratio <- rbind(metratio, met_issues) %>% 
  mutate(Fe_ratio = SFe_mgL/TFe_mgL,
         Mn_ratio = SMn_mgL/TMn_mgL)

metDates <- met %>% 
  select(Reservoir, DateTime, Year) %>% 
  unique()

metDates$MDay <- format(metDates$DateTime,"%m-%d")
  metDates$MDay <- as.Date(metDates$MDay, "%m-%d")
```

```{r Make TMn plot}
wer <- data.frame(
  data= c(rep("met",12)),
  var = c(rep("TMn_mgL",12)),
  Res = c(rep("FCR",6), rep("BVR",6)),
  Years = c(rep(2018:2023,2))
)

system.time(sd <- wer%>%
             pmap(heat_interp))

#Bind all the QAQC files from above
   temp_df <- dplyr::bind_rows(sd)

  temp_df <- temp_df%>%
    filter(!is.na(Reservoir),
           y>0.1)

# GEt the month and date for easier graphing. This is not the correct date.   
temp_df$MDay <- format(temp_df$Date,"%m-%d")
temp_df$MDay <- as.Date(temp_df$MDay, "%m-%d")

# make the plot

p1 <- make_metals_heat_map(
  data= temp_df,
  sample_dates = metDates,
  turnovers = turnover, 
  y_lim = c(0,2.5),
  custom_heatmap_palette = blue2green2red(60),
  y_units = "mg/L"
) + ggtitle('Total Mn')

```

```{r Make SMn plot}
wer <- data.frame(
  data= c(rep("met",12)),
  var = c(rep("SMn_mgL",12)),
  Res = c(rep("FCR",6), rep("BVR",6)),
  Years = c(rep(2018:2023,2))
)

system.time(sd <- wer%>%
             pmap(heat_interp))

#Bind all the QAQC files from above
   temp_df <- dplyr::bind_rows(sd)

  temp_df <- temp_df%>%
    filter(!is.na(Reservoir),
           y>0.1)

# GEt the month and date for easier graphing. This is not the correct date.   
temp_df$MDay <- format(temp_df$Date,"%m-%d")
temp_df$MDay <- as.Date(temp_df$MDay, "%m-%d")

# make the plot

p2 <- make_metals_heat_map(
  data= temp_df,
  sample_dates = metDates,
  turnovers = turnover, 
  y_lim = c(0,2.5),
  custom_heatmap_palette = blue2green2red(60),
  y_units = "mg/L"
) + ggtitle('Soluble Mn')

```

```{r}
MnPlot <- ggarrange(p1, p2, ncol = 1, labels = c('A', 'B'), common.legend = TRUE,
                    legend = 'bottom')
MnPlot
ggsave(MnPlot, filename = "figures/SedTraps_Mn_2018_2023.png", height = 6, width = 8, units = 'in')
```

```{r Make TFe plot}
wer <- data.frame(
  data= c(rep("met",12)),
  var = c(rep("TFe_mgL",12)),
  Res = c(rep("FCR",6), rep("BVR",6)),
  Years = c(rep(2018:2023,2))
)

system.time(sd <- wer%>%
             pmap(heat_interp))

#Bind all the QAQC files from above
   temp_df <- dplyr::bind_rows(sd)

  temp_df <- temp_df%>%
    filter(!is.na(Reservoir),
           y>0.1)

# GEt the month and date for easier graphing. This is not the correct date.   
temp_df$MDay <- format(temp_df$Date,"%m-%d")
temp_df$MDay <- as.Date(temp_df$MDay, "%m-%d")

# make the plot

p3 <- make_metals_heat_map(
  data= temp_df,
  sample_dates = metDates,
  turnovers = turnover, 
  y_lim = c(0,20),
  custom_heatmap_palette = blue2green2red(60),
  y_units = "mg/L"
) + ggtitle('Total Fe')

```

```{r Make SFe plot}
wer <- data.frame(
  data= c(rep("met",12)),
  var = c(rep("SFe_mgL",12)),
  Res = c(rep("FCR",6), rep("BVR",6)),
  Years = c(rep(2018:2023,2))
)

system.time(sd <- wer%>%
             pmap(heat_interp))

#Bind all the QAQC files from above
   temp_df <- dplyr::bind_rows(sd)

  temp_df <- temp_df%>%
    filter(!is.na(Reservoir),
           y>0.1)

# GEt the month and date for easier graphing. This is not the correct date.   
temp_df$MDay <- format(temp_df$Date,"%m-%d")
temp_df$MDay <- as.Date(temp_df$MDay, "%m-%d")

# make the plot

p4 <- make_metals_heat_map(
  data= temp_df,
  sample_dates = metDates,
  turnovers = turnover, 
  y_lim = c(0,20),
  custom_heatmap_palette = blue2green2red(60),
  y_units = "mg/L"
) + ggtitle('Soluble Fe')

```

```{r}
FePlot <- ggarrange(p3, p4, ncol = 1, labels = c('A', 'B'), common.legend = TRUE,
                    legend = 'bottom')
FePlot
ggsave(FePlot, filename = "figures/SedTraps_Fe_2018_2023.png", height = 6, width = 8, units = 'in')
```

### 2025-04-22 Manuscript1_figures.Rmd
Adding R project, scripts to process data and generate figures, and all helper csv's

---
title: "Manuscript1_figures"
author: "CEW"
date: "2024-11-14"
output: 
  html_document:
  df_print: paged

---

Includes figures 6-9, S1, S3, and S4
```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(pacman)
pacman::p_load(tidyverse, readxl, stringr, readr, glmnet, ISLR, lubridate, ggplot2, ggpubr, stats, gridExtra, graphics, gt)
```

```{r pull in all data, eval=TRUE, include=FALSE}
metals_file <- read_csv('https://pasta.lternet.edu/package/data/eml/edi/455/8/9c8c61b003923f4f03ebfe55cea8bbfd')

fluxes <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/1474/8/7cc135d14d92911eb7e8f6ceb096a29d")

FCRDO <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/271/8/fbb8c7a0230f4587f1c6e11417fe9dce")

BVRDO1 <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/725/5/f649de0e8a468922b40dcfa34285055e")

BVRDO2 <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/725/5/b7f0524aee78dcf4a2452a203a39c1f2")
```

```{r}
#set up file path for figures, change if necessary
myFilePath <- './figures'
```

## Seasonal Flux Paired T-Test Plot (Figure 6)

```{r Fig 6 and 7 set up, eval=TRUE, include=FALSE}
 fluxes2018_2023 <-  fluxes %>% 
  select(Reservoir, Date, Depth_m, Duration_days, TFeFlux_gm2d, TMnFlux_gm2d) %>% 
  na.omit() %>%
  mutate(Layer = if_else(Depth_m <= 5, 'Epilimnion', 'Hypolimnion'),
         Year = year(Date))

avgFluxes2018_2023 <- fluxes2018_2023 %>% 
  group_by(Reservoir, Date, Depth_m, Layer, Year) %>% 
  summarise(Duration_days = mean(Duration_days),
            AvgTFeFlux_gm2d = mean(TFeFlux_gm2d, na.rm = TRUE),
            AvgTMnFlux_gm2d = mean(TMnFlux_gm2d, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(TO = NA,
         #2018, only include data points from FCR that match data points from BVR
         TO = if_else(Reservoir == 'FCR' & Layer == 'Epilimnion' 
                      & Date < as.Date('2018-09-03'), 'Pre_', TO),
         TO = if_else(Reservoir == 'FCR' & Layer == 'Hypolimnion' 
                      & Date < as.Date('2018-07-23'), 'Pre_', TO),
         TO = if_else(Reservoir == 'FCR' & Layer == 'Epilimnion' 
                      & between(Date, as.Date('2018-09-03'), as.Date('2018-10-21')), 'Pre', TO),
         TO = if_else(Reservoir == 'FCR' & Layer == 'Hypolimnion' 
                      & between(Date, as.Date('2018-07-23'), as.Date('2018-10-21')), 'Pre', TO),
         TO = if_else(Year == 2018 & Reservoir == 'BVR' 
                      & Date <= as.Date('2018-09-07'), 'Pre', TO),
         TO = if_else(Year == 2018 & Reservoir == 'FCR' 
                      & Date >= as.Date('2018-10-21'), 'Post', TO),
         TO = if_else(Year == 2018 & Reservoir == 'BVR' 
                      & Date >= as.Date('2018-10-21'), 'Post', TO),
         #2019
         TO = if_else(Year == 2019 & Reservoir == 'FCR' & Date < as.Date('2019-10-24'), 'Pre', TO),
         TO = if_else(Year == 2019 & Reservoir == 'BVR' & Date < as.Date('2019-10-30'), 'Pre', TO),
         TO = if_else(Year == 2019 & Reservoir == 'FCR' & Date >= as.Date('2019-10-24'), 'Post', TO),
         TO = if_else(Year == 2019 & Reservoir == 'BVR' & Date >= as.Date('2019-10-30'), 'Post', TO),
         #2020
         TO = ifelse(Year == 2020 & Reservoir == 'FCR' & Date < as.Date('2020-11-02'), 'Pre', TO),
         TO = ifelse(Year == 2020 & Reservoir == 'BVR' & Date < as.Date('2020-11-02'), 'Pre', TO),
         TO = ifelse(Year == 2020 & Reservoir == 'FCR' & Date >= as.Date('2020-11-02'), 'Post', TO),
         TO = ifelse(Year == 2020 & Reservoir == 'BVR' & Date >= as.Date('2020-11-02'), 'Post', TO),
         #2021
         TO = ifelse(Year == 2021 & Reservoir == 'FCR' & Date < as.Date('2021-11-03'), 'Pre', TO),
         TO = ifelse(Year == 2021 & Reservoir == 'BVR' & Date < as.Date('2021-11-05'), 'Pre', TO),
         TO = ifelse(Year == 2021 & Reservoir == 'FCR' & Date >= as.Date('2021-11-03'), 'Post', TO),
         TO = ifelse(Year == 2021 & Reservoir == 'BVR' & Date >= as.Date('2021-11-05'), 'Post', TO),
         #2022
         TO = ifelse(Year == 2022 & Reservoir == 'FCR' & Date < as.Date('2022-10-20'), 'Pre', TO),
         TO = ifelse(Year == 2022 & Reservoir == 'BVR' & Date < as.Date('2022-10-19'), 'Pre', TO),
         TO = ifelse(Year == 2022 & Reservoir == 'FCR' & Date >= as.Date('2022-10-20'), 'Post', TO),
         TO = ifelse(Year == 2022 & Reservoir == 'BVR' & Date >= as.Date('2022-10-19'), 'Post', TO),
         #2023
         TO = ifelse(Year == 2023 & Reservoir == 'FCR' & Date < as.Date('2023-11-02'), 'Pre', TO),
         TO = ifelse(Year == 2023 & Reservoir == 'BVR' & Date < as.Date('2023-11-02'), 'Pre', TO),
         TO = ifelse(Year == 2023 & Reservoir == 'FCR' & Date >= as.Date('2023-11-02'), 'Post', TO),
         TO = ifelse(Year == 2023 & Reservoir == 'BVR' & Date >= as.Date('2023-11-02'), 'Post', TO)) %>% 
  arrange(Date)

avgCumulFluxes2018_2023 <- avgFluxes2018_2023 %>% 
  filter(TO == 'Pre' & Layer == 'Hypolimnion') %>%
  group_by(Reservoir, Layer, Year) %>% 
  mutate(CumulFe_gm2 = cumsum(AvgTFeFlux_gm2d*Duration_days),
         CumulMn_gm2 = cumsum(AvgTMnFlux_gm2d*Duration_days),
         CumulDuration_days = cumsum(Duration_days))

CumulFluxSummary <- avgCumulFluxes2018_2023 %>%
  group_by(Reservoir, Layer, Year) %>% 
  summarise(CumulFe_gm2 = max(CumulFe_gm2),
            CumulMn_gm2 = max(CumulMn_gm2),
            Duration_days = sum(Duration_days),
            Date = max(Date)) %>% 
  mutate(FeFlux = round(CumulFe_gm2/Duration_days, digits = 3),
         MnFlux = round(CumulMn_gm2/Duration_days, digits = 3))

avgCumulFluxes2018_2023_long <- avgCumulFluxes2018_2023 %>% 
  select(-c(AvgTFeFlux_gm2d, AvgTMnFlux_gm2d)) %>% 
  pivot_longer(cols = 8:9, values_to = 'Fluxes_gm2', names_to = 'Metal')

CumulFluxSummary_long <- CumulFluxSummary %>% 
  pivot_longer(cols = 4:5, values_to = 'Fluxes_gm2', names_to = 'Metal') %>% 
  mutate(Metal = factor(Metal, levels = c('CumulFe_gm2', 'CumulMn_gm2'),
                        labels = c('Iron', 'Manganese')))
```

```{r Figure 6 script, eval=TRUE, include=FALSE}
CumulFePlot1 <- CumulFluxSummary %>% 
  ggplot() + theme_bw(base_size = 18) + ggtitle('Iron') + ylab('Fe Flux (g/m2d)') +
  geom_point(aes(x = Reservoir, y = FeFlux, color = as.factor(Year), shape = as.factor(Year)), size = 3) +
  #2018
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.209, yend = 1.196, alpha = 0.5,
               color = "#F8766D", linetype = 3) +
  #2019
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.661, yend = 1.398, alpha = 0.5,
               color = "#B79F00", linetype = 3) +
  #2020
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.276, yend = 1.676, alpha = 0.5,
               color = "#00BA38", linetype = 3) +
  #2021
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.775, yend = 1.776, alpha = 0.5,
               color = "#00BFC4", linetype = 3) +
  #2022
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.867, yend = 1.849, alpha = 0.5,
               color = "#619CFF", linetype = 3) +
  #2023
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.819, yend = 1.017, alpha = 0.5,
               color = "#F564E3", linetype = 3) +
  annotate(geom = 'text', x= 1.5, y = 1.8, label = '**', size = 12) +
  guides(color = guide_legend(title = 'Year'), shape = guide_legend(title = 'Year'))

CumulMnPlot1 <- CumulFluxSummary %>% 
  ggplot() + theme_bw(base_size = 18) + ggtitle('Manganese') + ylab('Mn Flux (g/m2d)') +
  geom_point(aes(x = Reservoir, y = MnFlux, color = as.factor(Year), shape = as.factor(Year)), size = 3) +
  #2018
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.019, yend = 0.033, alpha = 0.5,
               color = "#F8766D", linetype = 3) +
  #2019
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.011, yend = 0.033, alpha = 0.5,
               color = "#B79F00", linetype = 3) +
  #2020
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.005, yend = 0.021, alpha = 0.5,
               color = "#00BA38", linetype = 3) +
  #2021
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.00712359, yend = 0.01952869, alpha = 0.5,
               color = "#00BFC4", linetype = 3) +
  #2022
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.020, yend = 0.029, alpha = 0.5,
               color = "#619CFF", linetype = 3) +
  #2023
  geom_segment(x = 'BVR', xend = 'FCR', y = 0.014, yend = 0.068, alpha = 0.5,
               color = "#F564E3", linetype = 3) +
  annotate(geom = 'text', x= 1.5, y = 0.065, label = '*', size = 12) +
  guides(color = guide_legend(title = 'Year'), shape = guide_legend(title = 'Year'))

ComboFluxPlot <- ggarrange(CumulFePlot1, CumulMnPlot1, nrow = 1, common.legend = TRUE, legend = 'right')
```

```{r Figure 6, eval=TRUE, include=TRUE}
ComboFluxPlot
```

## Cumulative Sed Mass Plot (Figure 7)
```{r Figure 7 script, eval=TRUE, include=FALSE}
plot_vline <- read_csv('~/Documents/R Projects/Sed Traps/TO_Dates.csv') %>% 
  mutate(Date = as.Date(Date),
         Event = as.factor(Event),
         Reservoir = as.factor(Reservoir),
         Layer = 'Hypolimnion')

FCRTO_vline <- plot_vline %>% 
  filter(Reservoir == 'FCR')

BVRTO_vline <- plot_vline %>% 
  filter(Reservoir == 'BVR')

strat_vline <- read_csv('StratStart2018_2023.csv') %>% 
  select(year, start, site_id, method) %>% 
  rename('Reservoir' = 'site_id',
         'Year' = 'year',
         'Date' = 'start') %>% 
  mutate(Layer = 'Hypolimnion')

HOxBoxes <- read_csv('HOx_Ranges.csv') %>% 
  mutate(Group = rownames(.),
         Layer = 'Hypolimnion',
         Year = year(HOxOn),
         DOYon = yday(HOxOn),
         DOYoff = yday(HOxOff))

HypCumulFluxPlot <- avgCumulFluxes2018_2023_long %>% 
  filter(Layer == 'Hypolimnion') %>%
  mutate(Metal = factor(Metal, levels = c('CumulFe_gm2', 'CumulMn_gm2'),
                        labels = c('Iron', 'Manganese'))) %>%
  ggplot() + theme_bw() + theme(panel.grid = element_blank()) + 
  facet_grid(cols = vars(Year), rows = vars(Metal), scales = 'free', space = "free_x") +
  scale_x_date(date_labels = '%b', breaks = '2 months', name = 'Date') +
  scale_y_continuous(name = 'Cumulative Mass Removal (g/m2)', limits = c(0, NA)) +
  geom_rect(aes(xmin = HOxOn, xmax = HOxOff, group = Group), ymin = -Inf, ymax = Inf, data = HOxBoxes, alpha = 0.2) + #creates the HOx boxes
  geom_vline(xintercept = FCRTO_vline$Date, linetype = 1, colour = '#D55E00') +
  geom_vline(xintercept = BVRTO_vline$Date, linetype = 2, colour = '#56B4E9') +
  geom_point(aes(as.Date(Date), Fluxes_gm2, colour = Reservoir, shape = Reservoir), size = 2)
```

```{r Figure 7, eval=TRUE, include=TRUE}
HypCumulFluxPlot
```

## Fe and Mn Threshold Plot (Figure 8)

```{r Fig 8 & 9 set up, eval=TRUE, include=FALSE}
metals <- metals_file %>% 
  filter(metals_file$DateTime >= as.Date('2018-01-01'),
         Site == 50, Reservoir == 'FCR' | Reservoir == 'BVR') %>% 
  select(Reservoir, Site, DateTime, Depth_m, TFe_mgL, SFe_mgL, TMn_mgL, SMn_mgL,
         Flag_TFe_mgL, Flag_TMn_mgL, Flag_SFe_mgL, Flag_SMn_mgL) %>%
  filter(Flag_TFe_mgL != 8 & Flag_SFe_mgL != 8 & Flag_TFe_mgL != 68 & Flag_SFe_mgL != 68,
         Flag_TMn_mgL != 8 & Flag_SMn_mgL != 8 & Flag_TMn_mgL != 68 & Flag_SMn_mgL != 68) %>% 
  mutate(FeDiff = TFe_mgL - SFe_mgL,
         MnDiff = TMn_mgL - SMn_mgL,
         STFe = SFe_mgL/TFe_mgL,
         STMn = SMn_mgL/TMn_mgL,
         Date = date(DateTime),
         Layer = NA,
         Layer = ifelse(Reservoir == 'FCR' & Depth_m <= 4, 'Epilimnion', Layer),
         Layer = ifelse(Reservoir == 'FCR' & Depth_m >= 4, 'Hypolimnion', Layer),
         Layer = ifelse(Reservoir == 'BVR' & Depth_m <= 5, 'Epilimnion', Layer),
         Layer = ifelse(Reservoir == 'BVR' & Depth_m >= 5, 'Hypolimnion', Layer),
         Year = year(DateTime)) %>% 
  group_by(Reservoir, Site, Date, Layer) %>% 
  mutate(AvgSTFe = mean(STFe, na.rm = TRUE),
         AvgSTMn = mean(STMn, na.rm = TRUE)) %>% 
  filter(FeDiff >= -0.02,
         MnDiff >= -0.06)

metals2023 <- metals %>% 
  filter(Year == 2023,
         MnDiff > 0)

Mnissues <- metals %>% 
  filter(Year == 2023,
         MnDiff < 0) %>% 
  rename('test1' = 'TMn_mgL',
         'test2' = 'SMn_mgL') %>% 
  rename('TMn_mgL' = 'test2',
         'SMn_mgL' = 'test1') %>% 
  mutate(MnDiff = TMn_mgL - SMn_mgL)

metals2023 <- rbind(metals2023, Mnissues) %>% 
  mutate(STFe = SFe_mgL/TFe_mgL,
         STMn = SMn_mgL/TMn_mgL) %>% 
  mutate(TO = NA,
         TO = ifelse(Year == 2023 & Reservoir == 'FCR' & Date < as.Date('2023-11-02'), 'Pre', TO),
         TO = ifelse(Year == 2023 & Reservoir == 'BVR' & Date < as.Date('2023-11-02'), 'Pre', TO),
         TO = ifelse(Year == 2023 & Reservoir == 'FCR' & Date >= as.Date('2023-11-02'), 'Post', TO),
         TO = ifelse(Year == 2023 & Reservoir == 'BVR' & Date >= as.Date('2023-11-02'), 'Post', TO))

metals2020 <- metals %>% 
  filter(Year == 2020,
         MnDiff > 0)

Mnissues20 <- metals %>% 
  filter(Year == 2020,
         MnDiff < 0) %>% 
  rename('test1' = 'TMn_mgL',
         'test2' = 'SMn_mgL') %>% 
  rename('TMn_mgL' = 'test2',
         'SMn_mgL' = 'test1') %>% 
  mutate(MnDiff = TMn_mgL - SMn_mgL)

metals2020 <- rbind(metals2020, Mnissues20) %>% 
  mutate(STFe = SFe_mgL/TFe_mgL,
         STMn = SMn_mgL/TMn_mgL) %>% 
  mutate(TO = NA,
         TO = ifelse(Year == 2020 & Reservoir == 'FCR' & Date < as.Date('2020-11-02'), 'Pre', TO),
         TO = ifelse(Year == 2020 & Reservoir == 'BVR' & Date < as.Date('2020-11-02'), 'Pre', TO),
         TO = ifelse(Year == 2020 & Reservoir == 'FCR' & Date >= as.Date('2020-11-02'), 'Post', TO),
         TO = ifelse(Year == 2020 & Reservoir == 'BVR' & Date >= as.Date('2020-11-02'), 'Post', TO),)
```

```{r Figure 8 script, eval=TRUE, include=FALSE}
#first find threshold dates, threshold = 0.3 mg/L for TMn and 0.9 mg/L for TFe

FeMnConcLeadingAvg <- metals %>% 
  filter(Reservoir == 'FCR' & Depth_m == 9) %>% 
  group_by(Reservoir, Depth_m, Year) %>%
  summarise(FeThresh = (lead(TFe_mgL, n = 2, order_by = Date) +
              lead(TFe_mgL, n = 1, order_by = Date) + TFe_mgL)/3,
            MnThresh = (lead(TMn_mgL, n = 2, order_by = Date) + 
              lead(TMn_mgL, n = 1, order_by = Date) + TMn_mgL)/3,
            Date = Date) %>% 
  ungroup() %>% 
  pivot_longer(cols = 4:5, values_to = 'Value', names_to = 'Thresh') %>%
  filter(Thresh == 'FeThresh' & Value >= 0.9 | Thresh == 'MnThresh' & Value >= 0.3) %>%
  group_by(Year, Thresh) %>%
  slice_min(order_by = Date) %>% 
  ungroup() %>%
  pivot_wider(names_from = Thresh, values_from = Date) %>%
  group_by(Reservoir, Depth_m, Year) %>% 
  summarise(MnThresh = mean(MnThresh, na.rm = TRUE),
            FeThresh = mean(FeThresh, na.rm = TRUE)) %>% 
  arrange(Year)

StratStart <- read_csv('StratStart2018_2023.csv') %>% 
  select(-c(length, end, method)) %>% 
  rename('Year' = 'year', 'StratStart' = 'start', 'Reservoir' = 'site_id')

#First HOx activation dates, where HOx was activated for more than 7 days before deactivation, see Table 1 in manuscript
HOxOn <- HOxBoxes %>%
  mutate(Duration = HOxOff - HOxOn) %>% 
  filter(Duration >= 7) %>% 
  select(Reservoir, Year, HOxOn) %>% 
  group_by(Reservoir, Year) %>% 
  slice_min(order_by = HOxOn)

FeMnThresh <- FeMnConcLeadingAvg %>% 
  full_join(StratStart) %>% 
  full_join(HOxOn) %>% 
  mutate(StratHOxDiff = as.numeric(HOxOn - StratStart),
         DaysToMnThresh = as.numeric(MnThresh - StratStart),
         DaysToFeThresh = as.numeric(FeThresh - StratStart))

MnThreshPlot <- ggplot(FeMnThresh) +
  theme_bw(base_size = 18) + 
  scale_y_continuous(limits = c(-15,100)) +
  scale_x_continuous(limits = c(-20,120), breaks = c(-20, 0, 20, 40, 60, 80, 100, 120)) +
  geom_vline(xintercept = 0, linewidth = 0.2) + geom_hline(yintercept = 0, linewidth = 0.2) +
  geom_point(aes(StratHOxDiff, DaysToMnThresh, color = as.factor(Year), shape = as.factor(Year)), size = 5) +
  guides(color = guide_legend(title = 'Year'), shape = guide_legend(title = 'Year')) +
  xlab('Time of HOx Activation Relative to Stratification (days)') + ylab('Manganese')

FeThreshPlot <- ggplot(FeMnThresh) +
  theme_bw(base_size = 18) + 
  scale_y_continuous(limits = c(-15,100)) +
  scale_x_continuous(limits = c(-20,120), breaks = c(-20, 0, 20, 40, 60, 80, 100, 120)) + xlab(NULL) +
  geom_vline(xintercept = 0, linewidth = 0.2) + geom_hline(yintercept = 0, linewidth = 0.2) +
  geom_point(aes(StratHOxDiff, DaysToFeThresh, color = as.factor(Year), shape = as.factor(Year)), size = 5) +
  guides(color = guide_legend(title = 'Year'), shape = guide_legend(title = 'Year')) + 
  xlab('') + ylab('Iron')

ThreshPlot <- ggarrange(FeThreshPlot, MnThreshPlot, ncol = 1, common.legend = TRUE, legend = 'bottom')
ThreshPlotFinal <- annotate_figure(ThreshPlot, left = text_grob('Time to Exceed Water Quality Threshold (days)', rot = 90, size = 18, hjust = 0.4))
```

```{r Figure 8, eval=TRUE, include=TRUE}
plot(ThreshPlotFinal)
```

## 2023 and 2020 Comparison of 9m TFe, SFe, TMn, SMn in FCR (Figure 9)

```{r Fig 9 script, eval=TRUE, include=FALSE}
Fe23 <- metals2023 %>% 
  select(Reservoir, Date, Site, Layer, Year, Depth_m, TFe_mgL, SFe_mgL, TO) %>%
  rename('Total' = 'TFe_mgL', 'Soluble' = 'SFe_mgL') %>% 
  pivot_longer(cols = 7:8, names_to = 'Type', values_to = 'Fe_mgL') %>% 
  filter(Layer == 'Hypolimnion')

Mn23 <- metals2023 %>% 
  select(Reservoir, Date, Site, Layer, Year, Depth_m, TMn_mgL, SMn_mgL, TO) %>%
  rename('Total' = 'TMn_mgL', 'Soluble' = 'SMn_mgL') %>% 
  pivot_longer(cols = 7:8, names_to = 'Type', values_to = 'Mn_mgL') %>% 
  filter(Layer == 'Hypolimnion') %>% 
  mutate(Type = factor(Type, levels = c('Soluble', 'Total')))

Fe20 <- metals2020 %>% 
  select(Reservoir, Date, Site, Layer, Year, Depth_m, TFe_mgL, SFe_mgL, TO) %>%
  rename('Total' = 'TFe_mgL', 'Soluble' = 'SFe_mgL') %>% 
  pivot_longer(cols = 7:8, names_to = 'Type', values_to = 'Fe_mgL') %>% 
  filter(Layer == 'Hypolimnion')

Mn20 <- metals2020 %>% 
  select(Reservoir, Date, Site, Layer, Year, Depth_m, TMn_mgL, SMn_mgL, TO) %>%
  rename('Total' = 'TMn_mgL', 'Soluble' = 'SMn_mgL') %>% 
  pivot_longer(cols = 7:8, names_to = 'Type', values_to = 'Mn_mgL') %>% 
  filter(Layer == 'Hypolimnion')

Mn23Reg <- Mn23 %>% 
  filter(Type == 'Total' & Reservoir == 'FCR' & Depth_m == 9 & TO == 'Pre' & Date >= as.Date('2023-03-23'))

Mn20Reg <- Mn20 %>% 
  filter(Type == 'Total' & Reservoir == 'FCR' & Depth_m == 9 & TO == 'Pre' & Date >= as.Date('2020-03-11'))

HOx2023 <- HOxBoxes %>% 
  filter(Year == 2023)

HOx2020 <- HOxBoxes %>% 
  filter(Year == 2020)

#Linear regression lines for release from sediment
Coef20 <- coef(lm(Mn20Reg$Mn_mgL ~ Mn20Reg$Date))[2]
Int20 <- coef(lm(Mn20Reg$Mn_mgL ~ Mn20Reg$Date))[1]

Coef23 <- coef(lm(Mn23Reg$Mn_mgL ~ Mn23Reg$Date))[2]
Int23 <- coef(lm(Mn23Reg$Mn_mgL ~ Mn23Reg$Date))[1]

Mod20 <- lm(Mn20Reg$Mn_mgL ~ Mn20Reg$Date)
summary(Mod20)
Mod23 <- lm(Mn23Reg$Mn_mgL ~ Mn23Reg$Date)
summary(Mod23)

#plots for Figure 9
STFe1 <- Fe20 %>% 
  filter(Layer == 'Hypolimnion' & Depth_m == 9 & Reservoir == 'FCR', Year == 2020) %>% 
ggplot() + 
  theme_bw(base_size = 18) + theme(panel.grid = element_blank(), legend.title = element_blank()) + 
  scale_x_date(date_labels = '%b', breaks = '2 months') + 
  scale_y_continuous(limits = c(0,10.5), name = 'Fe (mg/L)') + 
  geom_rect(aes(xmin = HOxOn, xmax = HOxOff, group = Group), ymin = -Inf, ymax = Inf, data = HOx2020, alpha = 0.2) +
  geom_vline(xintercept = as.Date('2020-11-02'), alpha = 0.75, linetype = 2) +
  geom_line(aes(as.Date(Date), Fe_mgL, color = as.factor(Type))) + 
  geom_point(aes(Date, Fe_mgL, shape = as.factor(Type), color = as.factor(Type)), size = 2) +
  ggtitle('2020') + #plot title
  theme(plot.title = element_text(hjust = 0.5)) + #centers title
  xlab(NULL)

STMn1 <- Mn20 %>% 
  filter(Layer == 'Hypolimnion' & Depth_m == 9 & Reservoir == 'FCR', Year == 2020) %>% 
  ggplot() + 
  theme_bw(base_size = 18) + theme(panel.grid = element_blank(), legend.title = element_blank()) + 
  scale_x_date(date_labels = '%b', breaks = '2 months') + 
  scale_y_continuous(limits = c(0,2.2), name = 'Mn (mg/L)') + 
  geom_rect(aes(xmin = HOxOn, xmax = HOxOff, group = Group), ymin = -Inf, ymax = Inf, data = HOx2020, alpha = 0.2) +
  geom_vline(xintercept = as.Date('2020-11-02'), alpha = 0.75, linetype = 2) +
  geom_line(aes(as.Date(Date), Mn_mgL, color = as.factor(Type))) +
  geom_smooth(aes(as.Date(Date), Mn_mgL), color = 'black', method = 'lm', formula = 'y~x', se = FALSE, data = Mn20Reg) +
  geom_point(aes(Date, Mn_mgL, shape = as.factor(Type), color = as.factor(Type)), size = 2) + xlab('Date') + geom_label(aes(x = as.Date('2020-04-20'), y = 2, label = 'Slope = 0.006 mg/Ld'))

STFe2 <- Fe23 %>% 
  filter(Layer == 'Hypolimnion' & Depth_m == 9 & Reservoir == 'FCR', Year == 2023) %>% 
  ggplot() + theme_bw(base_size = 18) + theme(panel.grid = element_blank(), legend.title = element_blank()) + scale_x_date(date_labels = '%b', breaks = '2 months') + 
  scale_y_continuous(limits = c(0,10.5), name = NULL) + 
  geom_rect(aes(xmin = HOxOn, xmax = HOxOff, group = Group), ymin = -Inf, ymax = Inf, data = HOx2023, alpha = 0.2) +
  geom_vline(xintercept = as.Date('2023-11-02'), alpha = 0.75, linetype = 2) +
  geom_line(aes(as.Date(Date), Fe_mgL, color = as.factor(Type))) + 
  geom_point(aes(Date, Fe_mgL, shape = as.factor(Type), color = as.factor(Type)), size = 2) +
  ggtitle('2023') + #plot title
  theme(plot.title = element_text(hjust = 0.5)) + #centers title
  xlab(NULL)

STMn2 <- Mn23 %>% 
  filter(Layer == 'Hypolimnion' & Depth_m == 9 & Reservoir == 'FCR', Year == 2023) %>% 
  ggplot() + theme_bw(base_size = 18) + theme(panel.grid = element_blank(), legend.title = element_blank()) + scale_x_date(date_labels = '%b', breaks = '2 months') + 
  scale_y_continuous(limits = c(0,2.2), name = NULL) + 
  geom_rect(aes(xmin = HOxOn, xmax = HOxOff, group = Group), ymin = -Inf, ymax = Inf, data = HOx2023, alpha = 0.2) +
  geom_vline(xintercept = as.Date('2023-11-02'), alpha = 0.75, linetype = 2) +
  geom_smooth(aes(as.Date(Date), Mn_mgL), color = 'black',
              method = 'lm', formula = 'y~x', se = FALSE, data = Mn23Reg) +
  geom_line(aes(as.Date(Date), Mn_mgL, color = as.factor(Type))) + 
  geom_point(aes(Date, Mn_mgL, shape = as.factor(Type), color = as.factor(Type)), size = 2) + xlab('Date') + geom_label(aes(x = as.Date('2023-04-20'), y = 2, label = 'Slope = 0.008 mg/Ld'))

comboPlot1 <- ggarrange(STFe1, STFe2, STMn1, STMn2, ncol = 2, nrow = 2, common.legend = TRUE, legend = 'bottom')
```

```{r Figure 9, eval=TRUE, include=TRUE}
comboPlot1
```

## Flux Plot (Figure S1)

```{r Flux Plot Figure S1 script, eval=TRUE, include=FALSE}
avgFluxes2018_2023_long <-  avgFluxes2018_2023 %>% 
  pivot_longer(cols = c(7:8), values_to = 'Fluxes_gm2d', names_to = 'Metal')

FluxPlot <- avgFluxes2018_2023_long %>% 
  filter(Layer == 'Hypolimnion') %>% 
  mutate(Metal = factor(Metal, levels = c('AvgTFeFlux_gm2d', 'AvgTMnFlux_gm2d'),
                        labels = c('Iron', 'Manganese'))) %>% 
  ggplot() + theme_bw() + theme(panel.grid = element_blank()) + 
  facet_grid(cols = vars(Year), rows = vars(Metal), scales = 'free', space = "free_x") +
  scale_x_date(date_labels = '%b', breaks = '2 months') +
  scale_y_continuous(name = 'Sedimentation Fluxes (g/m2d)') +
  geom_rect(aes(xmin = HOxOn, xmax = HOxOff, group = Group), ymin = -Inf, ymax = Inf, data = HOxBoxes, alpha = 0.2) +
  geom_vline(xintercept = FCRTO_vline$Date, linetype = 1, colour = '#D55E00') +
  geom_vline(xintercept = BVRTO_vline$Date, linetype = 2, colour = '#56B4E9') +
  geom_line(aes(as.Date(Date), Fluxes_gm2d, colour = Reservoir)) +
  geom_point(aes(as.Date(Date), Fluxes_gm2d, colour = Reservoir, shape = Reservoir)) + xlab('Date')
```

```{r Figure S1, eval=TRUE, include=TRUE}
FluxPlot
```

## DO plot (Figure S3)

```{r DO plot Figure S3 script, eval=TRUE, include=FALSE}
#DO Plot

DO1 <- FCRDO %>%
  mutate(DateTime = as.POSIXct(DateTime, format = "%Y-%m-%d %H:%M:%S")) %>% 
  select(Reservoir, Site, DateTime, RDO_mgL_9_adjusted) %>% 
  mutate(Date = date(DateTime)) %>% 
  group_by(Reservoir, Site, Date) %>% 
  summarise(DO_mgL_9m = mean(RDO_mgL_9_adjusted, na.rm = TRUE)) %>% 
  mutate(across(c('DO_mgL_9m'), ~ifelse(is.nan(.), NA, .)),
         Year = year(Date)) %>% 
  pivot_longer(cols = 4, names_to = 'Depth_m', values_to = 'DO_mgL') %>%
  mutate(Depth_m = factor(Depth_m, levels = c('DO_mgL_9m'),
                          labels = c('9'))) %>% 
  drop_na()

DO2 <- BVRDO1 %>% 
  select(Reservoir, Site, DateTime, RDO_mgL_13) %>% 
  mutate(Date = date(DateTime)) %>% 
  group_by(Reservoir, Site, Date) %>% 
  summarise(DO_mgL_13m = mean(RDO_mgL_13, na.rm = TRUE)) %>% 
  mutate(across(c('DO_mgL_13m'), ~ifelse(is.nan(.), NA, .)),
         Year = year(Date)) %>% 
  pivot_longer(cols = 4, names_to = 'Depth_m', values_to = 'DO_mgL') %>%
  mutate(Depth_m = factor(Depth_m, levels = c('DO_mgL_13m'),
                          labels = c('13'))) %>% 
  drop_na()

DO3 <- BVRDO2 %>% 
  filter(DateTime >= as.Date('2018-01-01')) %>% 
  select(Reservoir, Site, DateTime, MiniDotDO_mgL_10) %>% 
  mutate(Date = date(DateTime)) %>% 
  group_by(Reservoir, Site, Date) %>% 
  summarise(DO_mgL_10m = mean(MiniDotDO_mgL_10, na.rm = TRUE)) %>% 
  mutate(across(c('DO_mgL_10m'), ~ifelse(is.nan(.), NA, .)),
         Year = year(Date)) %>% 
  pivot_longer(cols = 4, names_to = 'Depth_m', values_to = 'DO_mgL') %>%
  mutate(Depth_m = factor(Depth_m, levels = c('DO_mgL_10m'),
                          labels = c('10')))

DO <- DO1 %>% 
  full_join(DO2) %>% 
  full_join(DO3) %>% 
  filter(Date <= as.Date('2023-12-31')) %>% 
  arrange(Date)

DO_plot1 <- DO %>% 
  ggplot() +
  scale_x_date(name = '', date_breaks = '1 year', date_labels = '%Y') +
  theme_bw(base_size = 18) + theme(panel.grid = element_blank()) +
  geom_path(aes(x = Date, y = DO_mgL, color = Reservoir)) + 
  ylab('Dissolved Oxygen (mg/L)')
```

```{r Figure S3, eval=TRUE, include=TRUE}
DO_plot1
```

## DO on HOx Activation Day Plot (Figure S4)
```{r DO plot figure S4 script, eval=TRUE, include=FALSE}
DOps1 <- FCRDO %>%
  select(Reservoir, Site, DateTime, RDOsat_percent_9_adjusted) %>% 
  mutate(Date = date(DateTime)) %>%
  group_by(Reservoir, Site, Date) %>% 
  summarise(AvgDOsat_percent_9 = mean(RDOsat_percent_9_adjusted, na.rm = TRUE)) %>% 
  ungroup() %>% #now select first HOx activation dates
  filter(Date == as.Date('2018-04-23') | Date == as.Date('2019-06-03') | 
           Date == as.Date('2020-06-29') | Date == as.Date('2021-06-11') |
           Date == as.Date('2022-05-19') | Date == as.Date('2023-03-06')) %>% 
  mutate(Year = year(Date))

DO_CumulMetalMass <- CumulFluxSummary %>%
  ungroup() %>% 
  filter(Reservoir == 'FCR',
         Year >= 2019) %>% 
  select(Reservoir, Year, FeFlux, MnFlux) %>% 
  full_join(DOps1)

DO_CumulMetal_Feplot <- DO_CumulMetalMass %>% 
  ggplot() + theme_bw(base_size = 18) +
  geom_point(aes(x = AvgDOsat_percent_9, y = FeFlux, color = as.factor(Year),
                 shape = as.factor(Year)), size = 3) +
  ylab('Seasonal Flux (g/m2d)') + xlab('') +
  guides(color = guide_legend(title = 'Year'), shape = guide_legend(title = 'Year')) +
  ggtitle('Iron')

DO_CumulMetal_Mnplot <- DO_CumulMetalMass %>% 
  ggplot() + theme_bw(base_size = 18) +
  geom_point(aes(x = AvgDOsat_percent_9, y = MnFlux, color = as.factor(Year),
                 shape = as.factor(Year)), size = 3) +
  ylab('') + xlab('') +
  guides(color = guide_legend(title = 'Year'), shape = guide_legend(title = 'Year')) +
  ggtitle('Manganese')

DO_CumulMetal_plot1 <- ggarrange(DO_CumulMetal_Feplot, DO_CumulMetal_Mnplot, nrow = 1,
                                common.legend = TRUE, legend = 'right', 
                                labels = c('A', 'B'))
DO_CumulMetal_plotFinal <- annotate_figure(DO_CumulMetal_plot1, bottom = text_grob('Dissolved Oxygen at HOx Activation (% saturation)', size = 18, hjust = 0.53, vjust = -1))
```

```{r Figure S4, eval=TRUE, include=TRUE}
DO_CumulMetal_plotFinal
```

## Tables
```{r Tables script, eval=TRUE, include=FALSE}
AvgFluxSummary2018_2023 <- avgFluxes2018_2023 %>% 
  filter(TO == 'Pre') %>% 
  group_by(Reservoir, Layer) %>% 
  summarise(MeanFeFlux = round(mean(AvgTFeFlux_gm2d, na.rm = T), digits = 3),
            MeanMnFlux = round(mean(AvgTMnFlux_gm2d, na.rm = T), digits = 3),
            MedianFeFlux = round(median(AvgTFeFlux_gm2d, na.rm = T), digits = 3),
            MedianMnFlux = round(median(AvgTMnFlux_gm2d, na.rm = T), digits = 3),
            MinFeFlux = round(min(AvgTFeFlux_gm2d, na.rm = T), digits = 3),
            MaxFeFlux = round(max(AvgTFeFlux_gm2d, na.rm = T), digits = 3),
            MinMnFlux = round(min(AvgTMnFlux_gm2d, na.rm = T), digits = 3),
            MaxMnFlux = round(max(AvgTMnFlux_gm2d, na.rm = T), digits = 3)) %>% 
  ungroup()

metals_HOx <- metals %>%
  filter(Reservoir == 'FCR' & Layer == 'Hypolimnion') %>% 
  mutate(HOx = 'Off',
         HOx = if_else(Year == 2018 & 
                         between(Date, as.Date('2018-04-23'), as.Date('2018-07-30')), 'On', HOx),
         HOx = if_else(Year == 2018 & 
                         between(Date, as.Date('2018-08-09'), as.Date('2018-09-10')), 'On', HOx),
         HOx = if_else(Year == 2019 & 
                         between(Date, as.Date('2019-06-03'), as.Date('2019-06-17')), 'On', HOx),
         HOx = if_else(Year == 2019 & 
                         between(Date, as.Date('2019-07-08'), as.Date('2019-07-19')), 'On', HOx),
         HOx = if_else(Year == 2019 & 
                         between(Date, as.Date('2019-08-05'), as.Date('2019-08-19')), 'On', HOx),
         HOx = if_else(Year == 2019 & 
                         between(Date, as.Date('2019-09-02'), as.Date('2019-12-01')), 'On', HOx),
         HOx = if_else(Year == 2020 & 
                         between(Date, as.Date('2020-06-29'), as.Date('2020-07-12')), 'On', HOx),
         HOx = if_else(Year == 2020 & 
                         between(Date, as.Date('2020-07-13'), as.Date('2020-07-22')), 'On', HOx),
         HOx = if_else(Year == 2020 & 
                         between(Date, as.Date('2020-07-23'), as.Date('2020-09-11')), 'On', HOx),
         HOx = if_else(Year == 2020 & 
                         between(Date, as.Date('2020-09-25'), as.Date('2020-12-02')), 'On', HOx),
         HOx = if_else(Year == 2021 & 
                         between(Date, as.Date('2021-06-11'), as.Date('2021-06-26')), 'On', HOx),
         HOx = if_else(Year == 2021 & 
                         between(Date, as.Date('2021-06-30'), as.Date('2021-07-08')), 'On', HOx),
         HOx = if_else(Year == 2021 & 
                         between(Date, as.Date('2021-07-12'), as.Date('2021-07-14')), 'On', HOx),
         HOx = if_else(Year == 2021 & 
                         between(Date, as.Date('2021-07-26'), as.Date('2021-09-06')), 'On', HOx),
         HOx = if_else(Year == 2021 & 
                         between(Date, as.Date('2021-09-14'), as.Date('2021-12-06')), 'On', HOx),
         HOx = if_else(Year == 2022 & 
                         between(Date, as.Date('2022-03-22'), as.Date('2022-03-24')), 'On', HOx),
         HOx = if_else(Year == 2022 & 
                         between(Date, as.Date('2022-03-29'), as.Date('2022-04-03')), 'On', HOx),
         HOx = if_else(Year == 2022 & 
                         between(Date, as.Date('2022-03-22'), as.Date('2022-03-24')), 'On', HOx),
         HOx = if_else(Year == 2022 & 
                         between(Date, as.Date('2022-05-19'), as.Date('2022-06-14')), 'On', HOx),
         HOx = if_else(Year == 2022 & 
                         between(Date, as.Date('2022-06-21'), as.Date('2022-08-26')), 'On', HOx),
         HOx = if_else(Year == 2022 & 
                         between(Date, as.Date('2022-08-29'), as.Date('2022-10-01')), 'On', HOx),
         HOx = if_else(Year == 2022 & 
                         between(Date, as.Date('2022-10-03'), as.Date('2022-12-12')), 'On', HOx),
         HOx = if_else(Year == 2023 & 
                         between(Date, as.Date('2023-03-06'), as.Date('2023-12-04')), 'On', HOx)) %>% 
  group_by(Reservoir, Layer, HOx) %>% 
  summarise(AvgSTFe = round(mean(SFe_mgL/TFe_mgL, na.rm = TRUE), digits = 3),
            AvgSTMn = round(mean(SMn_mgL/TMn_mgL, na.rm = TRUE), digits = 3)) %>% 
  ungroup()
```

```{r Tables, eval=TRUE, include=TRUE}
gt(AvgFluxSummary2018_2023)
gt(metals_HOx)
```

```{r Save all figures to folder if desired, eval=FALSE}
#Figure 6
ggsave(plot = ComboFluxPlot, filename = 'CumulHypFlux_tTest_2018-2023.png', path = myFilePath, height = 4, width = 8, units = 'in')
#Figure 7
ggsave(plot = HypCumulFluxPlot, filename = 'CumulHypFlux_HOxBoxes_2018-2023.png', path = myFilePath, height = 4, width = 8, units = 'in')
#Figure 8
ggsave(ThreshPlotFinal, file = 'HOxTimingFeMn.png', path = myFilePath, height = 8, width = 8, units = 'in')
#Figure 9
ggsave(comboPlot1, file = 'STFeMn_2020_2023.png', path = myFilePath, height = 6, width = 8, units = 'in')
#Figure S1
ggsave(plot = FluxPlot, filename = 'Flux_HOxBoxes_2018-2023.png', path = myFilePath, height = 4, width = 8, units = 'in')
#Figure S3
ggsave(DO_plot1, file = 'HypolimnionDO_2018_2023.png', path = myFilePath, height = 4, 
       width = 6, units = 'in')
#Figure S4
ggsave(DO_CumulMetal_plotFinal, file = 'DOps_SeasonalFlux.png', path = myFilePath,
       height = 4, width = 8, units = 'in')
```

### 2025-05-06 ABP_heatmap_for_Cece_20241018.Rmd
Revising scripts to include all figures

@@
 ---
-title: "Cece Sed Traps Manuscript Heat Map"
+title: "Manuscript Heat Map Script"
 author: "Adrienne Breef-Pilz"
@@
 ---
+
+Includes script for making Figures 2-5 and S2. Script written by ABP and updated by CEW. Edits include code chunks written by CEB.
 
@@
   read_csv("https://pasta.lternet.edu/package/data/eml/edi/200/14/0432a298a90b2b662f26c46071f66b8a")%>%
-  #read_csv("./../../Raw_CTD/ctd_L1.csv")|>
    filter(DateTime>ymd_hms("2018-01-01 00:00:00") & DateTime<ymd_hms("2023-12-31 00:00:00"))%>%
@@
 ```{r Turnover}
-
-### Still working on this
 
@@
 
-```{r Need to add in handhelp pH obs}
-
-ph <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/198/12/e0181372c6d4cbc66eca4644f8385470" )|>
-  #read_csv("./../../../DataAlreadyUploadedToEDI/EDIProductionFiles/MakeEMLYSI_PAR_secchi/2023/YSI_PAR_profiles_2013_2023.csv")|>
-  filter(DateTime>as.Date("2018-01-01"))|>
-  filter(Reservoir=="BVR"|Reservoir=="FCR")|>
-   filter(Site==50)|>
-  select(Reservoir, DateTime, Depth_m, pH)|>
-  drop_na(pH)|>
-  mutate(Year=year(DateTime))
-
-# bind with the CTD
-
-EDI_CTD_ph <- dplyr::bind_rows(EDI_CTD,ph)
-
-CTD_casts_ph <- ph|>
-  select(Reservoir, DateTime, Year)|>
-  mutate(DateTime = as.Date(DateTime))|>
-  unique()%>%
-  dplyr::bind_rows(. , CTD_casts)
-
-# GEt the month and date for easier graphing. This is not the correct date.   
-  CTD_casts_ph$MDay <- format(CTD_casts_ph$DateTime,"%m-%d")
-  CTD_casts_ph$MDay <- as.Date(CTD_casts_ph$MDay, "%m-%d")
-```
-
-```{r Make pH plot}
-
-##Need to fix this
-
- EDI_CTD_pH <- EDI_CTD|>
-   select(Reservoir, DateTime, Year, Depth_m, pH)%>%
-  bind_rows(.,ph)
-
-wer <- data.frame(
-  data= c(rep("EDI_CTD_pH",12)),
-  var = c(rep("pH",12)),
-  Res = c(rep("FCR",6), rep("BVR",6)),
-  Years = c(rep(2018:2023,2))
-)
-
-system.time(sd <- wer%>%
-             pmap(heat_interp))
-
-#Bind all the QAQC files from above
-   temp_df <- dplyr::bind_rows(sd)
-
-  temp_df <- temp_df%>%
-    filter(!is.na(Reservoir),
-           y>0.1)
-
-# GEt the month and date for easier graphing. This is not the correct date.   
-  temp_df$MDay <- format(temp_df$Date,"%m-%d")
-temp_df$MDay <- as.Date(temp_df$MDay, "%m-%d")
-
-# make the plot
-
-make_heat_map(
-  data= temp_df,
-  sample_dates = CTD_casts_ph,
-  turnovers = turnover,
-  y_lim = c(5,10),
-  custom_heatmap_palette = blue2green2red(60),
-  y_units = "pH",
-  output_file = "figures/SedTraps_CTD_pH_2018_2023.jpeg"
-)
-
-```
-
-```{r metals plotting}
+```{r metals plotting script}
 
@@
   theme_bw(base_size = 18)
-  # labs(color = "")+
-  # geom_point(data = sensor_depth_plot, 
-  #            aes(x = Date, y = Sensor_depth), 
-  #            shape = 23, fill = "black", color = "white", size  =2.5)+
-  # geom_vline(data=lines,aes(xintercept = Dates), show.legend = F)+
-  # scale_linetype_manual(values = c("solid","84"),
-  #                       limits = c("Thermocline","Outtake pipe"),  
-  #                       name= NULL)+
 
@@
 
-```{r}
+```{r read in metals data}
 metals <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/455/8/9c8c61b003923f4f03ebfe55cea8bbfd")
@@
 ```
+
+## Soluble:Total Metal Heat Maps (Figure S2)
+
+```{r S:T metals plotting}
+
+make_metals_ratio_heat_map <- function(
+    data,
+    sample_dates,
+    turnovers, 
+    y_lim,
+    custom_heatmap_palette,
+    y_units){
+
+#Heatmap
+
+# change the plots dimensions  
+#jpeg(paste0(output_file),width = 8, height = 4, units = "in", res = 400)
+water_temp <- data%>%
+  mutate(x = as.Date(x, origin = "1970-01-01"),
+         Year = year(x))%>%
+  filter(!is.na(z))%>%
+  ggplot()+
+  geom_raster(aes(x=MDay, y=y,fill = z))+
+  geom_point(data = sample_dates, aes(x = MDay, y = 0.1, z = NULL), pch = '|', size = 2, color = "gray60") + #to mark cast dates 
+   geom_vline(data= turnovers, aes(xintercept=MDay) , linetype="solid", color="gray60", linewidth=0.5) +
+  labs(y = "Depth (m)") +
+  scale_x_date(expand = c(0,0)) +
+  scale_y_reverse(expand = c(0,0),
+                  breaks = c(0.0, 2.5, 5.0, 7.5)) +
+  #scale_y_continuous(expand = c(0,0))+
+  theme(panel.border = element_rect(fill = NA),
+        axis.title.x=element_blank()) +
+  scale_fill_gradientn(name = y_units,
+                       limits = y_lim,
+                       colours = custom_heatmap_palette)+
+  facet_grid(rows= vars(Reservoir),cols = vars(Year),
+             scales = "free_y",
+             space = "free"
+             )+
+  theme(panel.background = element_rect(fill = "white"),
+          panel.spacing = unit(0.05, "lines"),
+        legend.position = 'bottom',
+        panel.grid = element_blank())
+  theme_bw(base_size = 18)
+
+return(water_temp)
+dev.off()
+
+}
+```
+
+```{r Make S:T Fe plot}
+wer <- data.frame(
+  data= c(rep("metratio",12)),
+  var = c(rep("Fe_ratio",12)),
+  Res = c(rep("FCR",6), rep("BVR",6)),
+  Years = c(rep(2018:2023,2))
+)
+
+system.time(sd <- wer%>%
+             pmap(heat_interp))
+
+#Bind all the QAQC files from above
+   temp_df <- dplyr::bind_rows(sd)
+
+  temp_df <- temp_df%>%
+    filter(!is.na(Reservoir),
+           y>0.1)
+
+# GEt the month and date for easier graphing. This is not the correct date.   
+temp_df$MDay <- format(temp_df$Date,"%m-%d")
+temp_df$MDay <- as.Date(temp_df$MDay, "%m-%d")
+
+# make the plot
+
+p5 <- make_metals_ratio_heat_map(
+  data= temp_df,
+  sample_dates = metDates,
+  turnovers = turnover, 
+  y_lim = c(0,1),
+  custom_heatmap_palette = blue2red(60),
+  y_units = "Soluble:Total"
+) + ggtitle('Iron')
+
+```
+
+```{r Make S:T Mn plot}
+wer <- data.frame(
+  data= c(rep("metratio",12)),
+  var = c(rep("Mn_ratio",12)),
+  Res = c(rep("FCR",6), rep("BVR",6)),
+  Years = c(rep(2018:2023,2))
+)
+
+system.time(sd <- wer%>%
+             pmap(heat_interp))
+
+#Bind all the QAQC files from above
+   temp_df <- dplyr::bind_rows(sd)
+
+  temp_df <- temp_df%>%
+    filter(!is.na(Reservoir),
+           y>0.1)
+
+# GEt the month and date for easier graphing. This is not the correct date.   
+temp_df$MDay <- format(temp_df$Date,"%m-%d")
+temp_df$MDay <- as.Date(temp_df$MDay, "%m-%d")
+
+# make the plot
+
+p6 <- make_metals_ratio_heat_map(
+  data= temp_df,
+  sample_dates = metDates,
+  turnovers = turnover, 
+  y_lim = c(0,1),
+  custom_heatmap_palette = blue2red(60),
+  y_units = "Soluble:Total"
+) + ggtitle('Manganese')
+
+```
+
+```{r}
+STPlot <- ggarrange(p5, p6, ncol = 1, labels = c('A', 'B'), common.legend = TRUE,
+                    legend = 'bottom')
+STPlot
+ggsave(STPlot, filename = "figures/SedTraps_STRatio_2018_2023.png", height = 6, width = 8, units = 'in')
+```

### 2025-05-06 Manuscript1_figures.Rmd
Revising scripts to include all figures

@@
 
-Includes figures 6-9, S1, S3, and S4
+## Data sources:
+
+1.
+Schreiber, M.E., C.E.
+Wood, A.
+Breef-Pilz, C.E.
+Bauer, G.
+Haynie, R.
+Keverline, M.
+Kricheldorf, and E.
+Tipper.
+2024.
+Time series of total and soluble metal concentrations from Falling Creek Reservoir, Beaverdam Reservoir, and Carvins Cove Reservoir in southwestern Virginia, USA from 2014 through 2023 ver 8.
+Environmental Data Initiative.
+https://doi.org/10.6073/pasta/584b1daf7f1541bc595aa3a9dd71a2c7.
+
+2.
+Schreiber, M.E., C.E.
+Wood, C.E.
+Bauer, A.
+Breef-Pilz, G.K.
+Haynie, and E.M.
+Tipper.
+2024.
+Sediment trap time series data for Beaverdam Reservoir and Falling Creek Reservoir in southwestern Virginia, USA 2018 through 2023 ver 8.
+Environmental Data Initiative.
+https://doi.org/10.6073/pasta/5ee061465e62c29587042c58e7a91e13.
+
+3.
+Carey, C.C., A.
+Breef-Pilz, V.
+Daneshmand, A.D.
+Delany, and R.Q.
+Thomas.
+2024.
+Time series of high-frequency sensor data measuring water temperature, dissolved oxygen, pressure, conductivity, specific conductance, total dissolved solids, chlorophyll a, phycocyanin, fluorescent dissolved organic matter, and turbidity at discrete depths in Falling Creek Reservoir, Virginia, USA in 2018-2023 ver 8.
+Environmental Data Initiative.
+https://doi.org/10.6073/pasta/7541e8d297850be7c613d116156735a9.
+
+4.
+Carey, C.C.
+and A.
+Breef-Pilz.
+2025.
+Time series of high-frequency sensor data measuring water temperature, dissolved oxygen, conductivity, specific conductance, total dissolved solids, chlorophyll a, phycocyanin, fluorescent dissolved organic matter, and turbidity at discrete depths, and water level in Beaverdam Reservoir, Virginia, USA in 2009-2024 ver 5.
+Environmental Data Initiative.
+https://doi.org/10.6073/pasta/8f666b34c120aa5d2242964cf3147f90.
+
+5.
+Carey, C.C., A.
+Breef-Pilz, H.L.
+Wander, D.W.
+Howard, G.K.
+Haynie, M.K.
+Kricheldorf, S.
+Tannheiser, and E.M.
+Tipper.
+2025.
+Secchi depth data and discrete depth profiles of water temperature, dissolved oxygen, conductivity, specific conductance, photosynthetic active radiation, oxidation-reduction potential, and pH for Beaverdam Reservoir, Carvins Cove Reservoir, Falling Creek Reservoir, Gatewood Reservoir, and Spring Hollow Reservoir in southwestern Virginia, USA 2013-2024 ver 13.
+Environmental Data Initiative.
+https://doi.org/10.6073/pasta/0df2b12c947e52a8d0240a75d20bbc1e.
+
+## Figures 6-9, S1, S3, and S4
 ```{r setup, include=FALSE}
@@
 BVRDO2 <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/725/5/b7f0524aee78dcf4a2452a203a39c1f2")
+
+Handhelds  <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/198/13/e50a50d062ee73f4d85e4f20b360ce4f")
 ```
 
-```{r}
+```{r set up file path}
 #set up file path for figures, change if necessary
@@
 
-## Seasonal Flux Paired T-Test Plot (Figure 6)
+## Figure 6. DO at HOx Activation vs Max Fe and Mn concentrations
 
-```{r Fig 6 and 7 set up, eval=TRUE, include=FALSE}
+```{r DO plot figure 6 script, eval=TRUE, include=FALSE}
+
+#First HOx activation dates, where HOx was activated for more than 7 days before deactivation, see Table 1 in manuscript
+
+HOxBoxes <- read_csv('HOx_Ranges.csv') %>% 
+  mutate(Group = rownames(.),
+         Layer = 'Hypolimnion',
+         Year = year(HOxOn),
+         DOYon = yday(HOxOn),
+         DOYoff = yday(HOxOff))
+
+HOxOn <- HOxBoxes %>%
+  mutate(Duration = HOxOff - HOxOn) %>% 
+  filter(Duration >= 7) %>% 
+  select(Reservoir, Year, HOxOn) %>% 
+  group_by(Reservoir, Year) %>% 
+  slice_min(order_by = HOxOn)
+
+DOps1 <- FCRDO %>%
+  select(Reservoir, Site, DateTime, RDOsat_percent_9_adjusted) %>% 
+  mutate(Date = date(DateTime)) %>%
+  group_by(Reservoir, Site, Date) %>% 
+  summarise(AvgDOsat_percent_9 = mean(RDOsat_percent_9_adjusted, na.rm = TRUE)) %>% 
+  ungroup() %>% #now select first HOx activation dates
+  filter(Date == as.Date('2018-04-23') | Date == as.Date('2019-06-03') | 
+           Date == as.Date('2020-06-29') | Date == as.Date('2021-06-11') |
+           Date == as.Date('2022-05-19') | Date == as.Date('2023-03-06')) %>% 
+  mutate(Year = year(Date)) %>% 
+  rename('HOxStart' = 'Date')
+
+DO_Handhelds <- Handhelds %>% 
+  filter(Reservoir == 'FCR') %>% 
+  mutate(Date = date(DateTime),
+         Year = year(DateTime)) %>% #HOx activated on 2018-04-23 @ noon
+  filter(DateTime == as_datetime('2018-04-23 09:45:00') & Depth_m == 9) %>% 
+  select(Reservoir, Site, Date, Year, DOsat_percent) %>% 
+  rename('HOxStart' = 'Date',
+         'AvgDOsat_percent_9' = 'DOsat_percent')
+
+DOps2 <- DOps1 %>% 
+  full_join(DO_Handhelds)
+
+metals <- metals_file %>% 
+  filter(metals_file$DateTime >= as.Date('2018-01-01'),
+         Site == 50, Reservoir == 'FCR' | Reservoir == 'BVR') %>% 
+  select(Reservoir, Site, DateTime, Depth_m, TFe_mgL, SFe_mgL, TMn_mgL, SMn_mgL,
+         Flag_TFe_mgL, Flag_TMn_mgL, Flag_SFe_mgL, Flag_SMn_mgL) %>%
+  filter(Flag_TFe_mgL != 8 & Flag_SFe_mgL != 8 & Flag_TFe_mgL != 68 & Flag_SFe_mgL != 68,
+         Flag_TMn_mgL != 8 & Flag_SMn_mgL != 8 & Flag_TMn_mgL != 68 & Flag_SMn_mgL != 68) %>% 
+  mutate(FeDiff = TFe_mgL - SFe_mgL,
+         MnDiff = TMn_mgL - SMn_mgL,
+         STFe = SFe_mgL/TFe_mgL,
+         STMn = SMn_mgL/TMn_mgL,
+         Date = date(DateTime),
+         Layer = NA,
+         Layer = ifelse(Reservoir == 'FCR' & Depth_m <= 4, 'Epilimnion', Layer),
+         Layer = ifelse(Reservoir == 'FCR' & Depth_m >= 4, 'Hypolimnion', Layer),
+         Layer = ifelse(Reservoir == 'BVR' & Depth_m <= 5, 'Epilimnion', Layer),
+         Layer = ifelse(Reservoir == 'BVR' & Depth_m >= 5, 'Hypolimnion', Layer),
+         Year = year(DateTime)) %>% 
+  group_by(Reservoir, Site, Date, Layer) %>% 
+  mutate(AvgSTFe = mean(STFe, na.rm = TRUE),
+         AvgSTMn = mean(STMn, na.rm = TRUE)) %>% 
+  filter(FeDiff >= -0.02,
+         MnDiff >= -0.06)
+
+MaxMetals <- metals %>% 
+  filter(Year >= 2018 & Depth_m == 9 & Reservoir == 'FCR') %>% 
+  filter(Year == 2018 & between(Date, as.Date('2018-04-23'), as.Date('2018-08-12')) | #only include dates where HOx
+           Year == 2019 & between(Date, as.Date('2019-06-03'), as.Date('2019-11-20'))  | #was active
+           Year == 2020 & between(Date, as.Date('2020-06-29'), as.Date('2020-12-02')) |
+           Year == 2021 & between(Date, as.Date('2021-06-11'), as.Date('2021-12-06')) |
+           Year == 2022 & between(Date, as.Date('2022-05-19'), as.Date('2022-12-12')) |
+           Year == 2023 & between(Date, as.Date('2023-03-06'), as.Date('2023-12-04'))) %>% 
+  group_by(Reservoir, Site, Year) %>% 
+  summarise(MaxTFe_mgL = max(TFe_mgL),
+            MaxTMn_mgL = max(TMn_mgL))
+
+DO_MaxMetalMass <- DOps2 %>% 
+  full_join(MaxMetals)
+
+DO_MaxMetal_Feplot <- DO_MaxMetalMass %>% 
+  ggplot() + theme_bw(base_size = 18) +
+  geom_point(aes(x = AvgDOsat_percent_9, y = MaxTFe_mgL, color = as.factor(Year),
+                 shape = as.factor(Year)), size = 3) +
+  ylab('Maximum Concentration (mg/L)') + xlab('') +
+  guides(color = guide_legend(title = 'Year'), shape = guide_legend(title = 'Year')) +
+  ggtitle('Total Iron')
+
+DO_MaxMetal_Mnplot <- DO_MaxMetalMass %>% 
+  ggplot() + theme_bw(base_size = 18) +
+  geom_point(aes(x = AvgDOsat_percent_9, y = MaxTMn_mgL, color = as.factor(Year),
+                 shape = as.factor(Year)), size = 3) +
+  ylab('') + xlab('') +
+  guides(color = guide_legend(title = 'Year'), shape = guide_legend(title = 'Year')) +
+  ggtitle('Total Manganese')
+
+DO_MaxMetal_plot <- ggarrange(DO_MaxMetal_Feplot, DO_MaxMetal_Mnplot, nrow = 1, common.legend = TRUE,
+                              legend = 'right', labels = c('A', 'B'))
+DO_MaxMetal_plotFinal <- annotate_figure(DO_MaxMetal_plot, bottom = text_grob('Dissolved Oxygen at HOx Activation (% saturation)', size = 18, hjust = 0.53, vjust = -1))
+```
+
+```{r Figure 6, eval=TRUE, include=TRUE}
+DO_MaxMetal_plotFinal
+```
+
+## Figure 7. Seasonal Flux Paired T-Test Plot
+
+```{r Fig 7 and 8 set up, eval=TRUE, include=FALSE}
  fluxes2018_2023 <-  fluxes %>% 
@@
 
-```{r Figure 6 script, eval=TRUE, include=FALSE}
+```{r Figure 7 script, eval=TRUE, include=FALSE}
 CumulFePlot1 <- CumulFluxSummary %>% 
@@
 
-```{r Figure 6, eval=TRUE, include=TRUE}
+```{r Figure 7, eval=TRUE, include=TRUE}
 ComboFluxPlot
@@
 
-## Cumulative Sed Mass Plot (Figure 7)
-```{r Figure 7 script, eval=TRUE, include=FALSE}
+## Figure 8. Cumulative Sed Mass Plot
+```{r Figure 8 script, eval=TRUE, include=FALSE}
 plot_vline <- read_csv('~/Documents/R Projects/Sed Traps/TO_Dates.csv') %>% 
@@
 
-HOxBoxes <- read_csv('HOx_Ranges.csv') %>% 
-  mutate(Group = rownames(.),
-         Layer = 'Hypolimnion',
-         Year = year(HOxOn),
-         DOYon = yday(HOxOn),
-         DOYoff = yday(HOxOff))
-
 HypCumulFluxPlot <- avgCumulFluxes2018_2023_long %>% 
@@
 
-```{r Figure 7, eval=TRUE, include=TRUE}
+```{r Figure 8, eval=TRUE, include=TRUE}
 HypCumulFluxPlot
@@
 
-## Fe and Mn Threshold Plot (Figure 8)
+## Figure 9. 2023 and 2020 Comparison of 9m TFe, SFe, TMn, SMn in FCR
 
-```{r Fig 8 & 9 set up, eval=TRUE, include=FALSE}
-metals <- metals_file %>% 
-  filter(metals_file$DateTime >= as.Date('2018-01-01'),
-         Site == 50, Reservoir == 'FCR' | Reservoir == 'BVR') %>% 
-  select(Reservoir, Site, DateTime, Depth_m, TFe_mgL, SFe_mgL, TMn_mgL, SMn_mgL,
-         Flag_TFe_mgL, Flag_TMn_mgL, Flag_SFe_mgL, Flag_SMn_mgL) %>%
-  filter(Flag_TFe_mgL != 8 & Flag_SFe_mgL != 8 & Flag_TFe_mgL != 68 & Flag_SFe_mgL != 68,
-         Flag_TMn_mgL != 8 & Flag_SMn_mgL != 8 & Flag_TMn_mgL != 68 & Flag_SMn_mgL != 68) %>% 
-  mutate(FeDiff = TFe_mgL - SFe_mgL,
-         MnDiff = TMn_mgL - SMn_mgL,
-         STFe = SFe_mgL/TFe_mgL,
-         STMn = SMn_mgL/TMn_mgL,
-         Date = date(DateTime),
-         Layer = NA,
-         Layer = ifelse(Reservoir == 'FCR' & Depth_m <= 4, 'Epilimnion', Layer),
-         Layer = ifelse(Reservoir == 'FCR' & Depth_m >= 4, 'Hypolimnion', Layer),
-         Layer = ifelse(Reservoir == 'BVR' & Depth_m <= 5, 'Epilimnion', Layer),
-         Layer = ifelse(Reservoir == 'BVR' & Depth_m >= 5, 'Hypolimnion', Layer),
-         Year = year(DateTime)) %>% 
-  group_by(Reservoir, Site, Date, Layer) %>% 
-  mutate(AvgSTFe = mean(STFe, na.rm = TRUE),
-         AvgSTMn = mean(STMn, na.rm = TRUE)) %>% 
-  filter(FeDiff >= -0.02,
-         MnDiff >= -0.06)
-
+```{r Figure 9 set up, eval=TRUE, include=FALSE}
 metals2023 <- metals %>% 
@@
 
-```{r Figure 8 script, eval=TRUE, include=FALSE}
-#first find threshold dates, threshold = 0.3 mg/L for TMn and 0.9 mg/L for TFe
-
-FeMnConcLeadingAvg <- metals %>% 
-  filter(Reservoir == 'FCR' & Depth_m == 9) %>% 
-  group_by(Reservoir, Depth_m, Year) %>%
-  summarise(FeThresh = (lead(TFe_mgL, n = 2, order_by = Date) +
-              lead(TFe_mgL, n = 1, order_by = Date) + TFe_mgL)/3,
-            MnThresh = (lead(TMn_mgL, n = 2, order_by = Date) + 
-              lead(TMn_mgL, n = 1, order_by = Date) + TMn_mgL)/3,
-            Date = Date) %>% 
-  ungroup() %>% 
-  pivot_longer(cols = 4:5, values_to = 'Value', names_to = 'Thresh') %>%
-  filter(Thresh == 'FeThresh' & Value >= 0.9 | Thresh == 'MnThresh' & Value >= 0.3) %>%
-  group_by(Year, Thresh) %>%
-  slice_min(order_by = Date) %>% 
-  ungroup() %>%
-  pivot_wider(names_from = Thresh, values_from = Date) %>%
-  group_by(Reservoir, Depth_m, Year) %>% 
-  summarise(MnThresh = mean(MnThresh, na.rm = TRUE),
-            FeThresh = mean(FeThresh, na.rm = TRUE)) %>% 
-  arrange(Year)
-
-StratStart <- read_csv('StratStart2018_2023.csv') %>% 
-  select(-c(length, end, method)) %>% 
-  rename('Year' = 'year', 'StratStart' = 'start', 'Reservoir' = 'site_id')
-
-#First HOx activation dates, where HOx was activated for more than 7 days before deactivation, see Table 1 in manuscript
-HOxOn <- HOxBoxes %>%
-  mutate(Duration = HOxOff - HOxOn) %>% 
-  filter(Duration >= 7) %>% 
-  select(Reservoir, Year, HOxOn) %>% 
-  group_by(Reservoir, Year) %>% 
-  slice_min(order_by = HOxOn)
-
-FeMnThresh <- FeMnConcLeadingAvg %>% 
-  full_join(StratStart) %>% 
-  full_join(HOxOn) %>% 
-  mutate(StratHOxDiff = as.numeric(HOxOn - StratStart),
-         DaysToMnThresh = as.numeric(MnThresh - StratStart),
-         DaysToFeThresh = as.numeric(FeThresh - StratStart))
-
-MnThreshPlot <- ggplot(FeMnThresh) +
-  theme_bw(base_size = 18) + 
-  scale_y_continuous(limits = c(-15,100)) +
-  scale_x_continuous(limits = c(-20,120), breaks = c(-20, 0, 20, 40, 60, 80, 100, 120)) +
-  geom_vline(xintercept = 0, linewidth = 0.2) + geom_hline(yintercept = 0, linewidth = 0.2) +
-  geom_point(aes(StratHOxDiff, DaysToMnThresh, color = as.factor(Year), shape = as.factor(Year)), size = 5) +
-  guides(color = guide_legend(title = 'Year'), shape = guide_legend(title = 'Year')) +
-  xlab('Time of HOx Activation Relative to Stratification (days)') + ylab('Manganese')
-
-FeThreshPlot <- ggplot(FeMnThresh) +
-  theme_bw(base_size = 18) + 
-  scale_y_continuous(limits = c(-15,100)) +
-  scale_x_continuous(limits = c(-20,120), breaks = c(-20, 0, 20, 40, 60, 80, 100, 120)) + xlab(NULL) +
-  geom_vline(xintercept = 0, linewidth = 0.2) + geom_hline(yintercept = 0, linewidth = 0.2) +
-  geom_point(aes(StratHOxDiff, DaysToFeThresh, color = as.factor(Year), shape = as.factor(Year)), size = 5) +
-  guides(color = guide_legend(title = 'Year'), shape = guide_legend(title = 'Year')) + 
-  xlab('') + ylab('Iron')
-
-ThreshPlot <- ggarrange(FeThreshPlot, MnThreshPlot, ncol = 1, common.legend = TRUE, legend = 'bottom')
-ThreshPlotFinal <- annotate_figure(ThreshPlot, left = text_grob('Time to Exceed Water Quality Threshold (days)', rot = 90, size = 18, hjust = 0.4))
-```
-
-```{r Figure 8, eval=TRUE, include=TRUE}
-plot(ThreshPlotFinal)
-```
-
-## 2023 and 2020 Comparison of 9m TFe, SFe, TMn, SMn in FCR (Figure 9)
-
-```{r Fig 9 script, eval=TRUE, include=FALSE}
+```{r Figure 9 script, eval=TRUE, include=FALSE}
 Fe23 <- metals2023 %>% 
@@
 
-## Flux Plot (Figure S1)
+## Figure S1. Flux Plot
 
@@
 
-## DO plot (Figure S3)
+## Figure S3. DO plot
 
@@
   mutate(Depth_m = factor(Depth_m, levels = c('DO_mgL_9m'),
-                          labels = c('9'))) %>% 
+                          labels = c('9')),
+         Method = 'edi.271.9') %>% 
   drop_na()
@@
   mutate(Depth_m = factor(Depth_m, levels = c('DO_mgL_13m'),
-                          labels = c('13'))) %>% 
+                          labels = c('13')),
+         Method = 'edi.725.5') %>% 
   drop_na()
@@
   mutate(Depth_m = factor(Depth_m, levels = c('DO_mgL_10m'),
-                          labels = c('10')))
+                          labels = c('10')),
+         Method = 'edi.725.5') %>% 
+  drop_na()
+
+DO4 <- Handhelds %>% 
+  mutate(Date = date(DateTime),
+         Year = year(DateTime)) %>% #HOx activated on 2018-04-23 @ noon
+  filter(Year == 2018| Year == 2019 | Year == 2020,
+         Reservoir == 'BVR' & Depth_m == 10 & 
+           between(Date, as.Date('2018-05-04'), as.Date('2018-12-05'))|
+           Reservoir == 'BVR' & Depth_m == 10 & 
+           between(Date, as.Date('2019-05-18'), as.Date('2020-03-14'))|
+           Reservoir == 'BVR' & Depth_m == 10 & 
+           between(Date, as.Date('2020-05-16'), as.Date('2020-06-17'))|
+           Reservoir == 'FCR' & Depth_m == 9 & Date < as.Date('2018-08-19')) %>% 
+  select(Reservoir, Site, Date, Year, Depth_m, DO_mgL) %>% 
+  mutate(Depth_m = factor(Depth_m),
+         Method = 'edi.198.13') %>% 
+  drop_na()
 
@@
   full_join(DO3) %>%
+  full_join(DO4) %>% 
   filter(Date <= as.Date('2023-12-31')) %>%
+  mutate(Method = factor(Method, levels = c('edi.271.9', 'edi.725.5', 'edi.198.13'))) %>%
+  ungroup() %>% 
+  #add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2018-11-17'),
+  #        Year = 2018, Depth_m = as.factor(10), DO_mgL = NA, 
+  #        Method = as.factor('edi.198.13')) %>%
+  add_row(Reservoir = 'FCR', Site = 50, Date = as.Date('2018-08-19'),
+          Year = 2018, Depth_m = as.factor(9), DO_mgL = NA, 
+          Method = as.factor('edi.198.13')) %>%
+  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2018-12-05'),
+          Year = 2018, Depth_m = as.factor(10), DO_mgL = NA, 
+          Method = as.factor('edi.198.13')) %>%
+  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2019-05-17'),
+          Year = 2019, Depth_m = as.factor(10), DO_mgL = NA, 
+          Method = as.factor('edi.198.13')) %>%
+  #add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2019-10-18'),
+  #        Year = 2019, Depth_m = as.factor(10), DO_mgL = NA, 
+  #        Method = as.factor('edi.198.13')) %>%
+  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-01-01'),
+          Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
+          Method = as.factor('edi.725.5')) %>% 
+  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-03-15'),
+          Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
+          Method = as.factor('edi.198.13')) %>% 
+    add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-05-15'),
+          Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
+          Method = as.factor('edi.198.13')) %>%
+  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-06-05'),
+          Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
+          Method = as.factor('edi.198.13')) %>%
 arrange(Date)
@@
   theme_bw(base_size = 18) + theme(panel.grid = element_blank()) +
-  geom_path(aes(x = Date, y = DO_mgL, color = Reservoir)) + 
+  geom_line(aes(x = Date, y = DO_mgL, color = Reservoir, linetype = Method)) +
+  scale_linetype_manual(values = c('solid', 'solid', 'dotted')) + 
+  guides(linetype = guide_legend(title = 'Data Package')) +
   ylab('Dissolved Oxygen (mg/L)')
@@
 
-## DO on HOx Activation Day Plot (Figure S4)
+## Figure S4. DO on HOx Activation Day Plot
 ```{r DO plot figure S4 script, eval=TRUE, include=FALSE}
-DOps1 <- FCRDO %>%
-  select(Reservoir, Site, DateTime, RDOsat_percent_9_adjusted) %>% 
-  mutate(Date = date(DateTime)) %>%
-  group_by(Reservoir, Site, Date) %>% 
-  summarise(AvgDOsat_percent_9 = mean(RDOsat_percent_9_adjusted, na.rm = TRUE)) %>% 
-  ungroup() %>% #now select first HOx activation dates
-  filter(Date == as.Date('2018-04-23') | Date == as.Date('2019-06-03') | 
-           Date == as.Date('2020-06-29') | Date == as.Date('2021-06-11') |
-           Date == as.Date('2022-05-19') | Date == as.Date('2023-03-06')) %>% 
-  mutate(Year = year(Date))
 
-DO_CumulMetalMass <- CumulFluxSummary %>%
+HOxOnCumulFluxes2018_2023 <- avgFluxes2018_2023 %>% 
+  filter(TO == 'Pre' & Layer == 'Hypolimnion') %>%
+  filter(Year == 2018 & between(Date, as.Date('2018-04-23'), as.Date('2018-08-12')) | #only include dates where HOx
+           Year == 2019 & between(Date, as.Date('2019-06-03'), as.Date('2019-11-20'))  | #was active
+           Year == 2020 & between(Date, as.Date('2020-06-29'), as.Date('2020-12-02')) |
+           Year == 2021 & between(Date, as.Date('2021-06-11'), as.Date('2021-12-06')) |
+           Year == 2022 & between(Date, as.Date('2022-05-19'), as.Date('2022-12-12')) |
+           Year == 2023 & between(Date, as.Date('2023-03-06'), as.Date('2023-12-04'))) %>% 
+  group_by(Reservoir, Layer, Year) %>% 
+  mutate(CumulFe_gm2 = cumsum(AvgTFeFlux_gm2d*Duration_days),
+         CumulMn_gm2 = cumsum(AvgTMnFlux_gm2d*Duration_days),
+         CumulDuration_days = cumsum(Duration_days))
+
+HOxOnCumulFluxSummary <- HOxOnCumulFluxes2018_2023 %>%
+  group_by(Reservoir, Layer, Year) %>% 
+  summarise(CumulFe_gm2 = max(CumulFe_gm2),
+            CumulMn_gm2 = max(CumulMn_gm2),
+            Duration_days = sum(Duration_days),
+            Date = max(Date)) %>% 
+  mutate(FeFlux = round(CumulFe_gm2/Duration_days, digits = 3),
+         MnFlux = round(CumulMn_gm2/Duration_days, digits = 3))
+
+DO_CumulMetalMass <- HOxOnCumulFluxSummary %>%
   ungroup() %>% 
   filter(Reservoir == 'FCR',
-         Year >= 2019) %>% 
+         Year >= 2018) %>% 
   select(Reservoir, Year, FeFlux, MnFlux) %>% 
-  full_join(DOps1)
+  full_join(DOps2)
 
@@
 
-DO_CumulMetal_plot1 <- ggarrange(DO_CumulMetal_Feplot, DO_CumulMetal_Mnplot, nrow = 1,
-                                common.legend = TRUE, legend = 'right', 
+DO_CumulMetal_plot1 <- ggarrange(DO_CumulMetal_Feplot, DO_CumulMetal_Mnplot,
+                                 nrow = 1, common.legend = TRUE, legend = 'right', 
                                 labels = c('A', 'B'))
@@
 metals_HOx <- metals %>%
-  filter(Reservoir == 'FCR' & Layer == 'Hypolimnion') %>% 
+  filter(Layer == 'Hypolimnion') %>% 
   mutate(HOx = 'Off',
-         HOx = if_else(Year == 2018 & 
+         HOx = if_else(Year == 2018 & Reservoir == 'FCR' &
                          between(Date, as.Date('2018-04-23'), as.Date('2018-07-30')), 'On', HOx),
-         HOx = if_else(Year == 2018 & 
+         HOx = if_else(Year == 2018 & Reservoir == 'FCR' &
                          between(Date, as.Date('2018-08-09'), as.Date('2018-09-10')), 'On', HOx),
-         HOx = if_else(Year == 2019 & 
+         HOx = if_else(Year == 2019 & Reservoir == 'FCR' &
                          between(Date, as.Date('2019-06-03'), as.Date('2019-06-17')), 'On', HOx),
-         HOx = if_else(Year == 2019 & 
+         HOx = if_else(Year == 2019 & Reservoir == 'FCR' &
                          between(Date, as.Date('2019-07-08'), as.Date('2019-07-19')), 'On', HOx),
-         HOx = if_else(Year == 2019 & 
+         HOx = if_else(Year == 2019 & Reservoir == 'FCR' &
                          between(Date, as.Date('2019-08-05'), as.Date('2019-08-19')), 'On', HOx),
-         HOx = if_else(Year == 2019 & 
+         HOx = if_else(Year == 2019 & Reservoir == 'FCR' &
                          between(Date, as.Date('2019-09-02'), as.Date('2019-12-01')), 'On', HOx),
-         HOx = if_else(Year == 2020 & 
+         HOx = if_else(Year == 2020 & Reservoir == 'FCR' &
                          between(Date, as.Date('2020-06-29'), as.Date('2020-07-12')), 'On', HOx),
-         HOx = if_else(Year == 2020 & 
+         HOx = if_else(Year == 2020 & Reservoir == 'FCR' &
                          between(Date, as.Date('2020-07-13'), as.Date('2020-07-22')), 'On', HOx),
-         HOx = if_else(Year == 2020 & 
+         HOx = if_else(Year == 2020 & Reservoir == 'FCR' &
                          between(Date, as.Date('2020-07-23'), as.Date('2020-09-11')), 'On', HOx),
-         HOx = if_else(Year == 2020 & 
+         HOx = if_else(Year == 2020 & Reservoir == 'FCR' &
                          between(Date, as.Date('2020-09-25'), as.Date('2020-12-02')), 'On', HOx),
-         HOx = if_else(Year == 2021 & 
+         HOx = if_else(Year == 2021 & Reservoir == 'FCR' &
                          between(Date, as.Date('2021-06-11'), as.Date('2021-06-26')), 'On', HOx),
-         HOx = if_else(Year == 2021 & 
+         HOx = if_else(Year == 2021 & Reservoir == 'FCR' &
                          between(Date, as.Date('2021-06-30'), as.Date('2021-07-08')), 'On', HOx),
-         HOx = if_else(Year == 2021 & 
+         HOx = if_else(Year == 2021 & Reservoir == 'FCR' &
                          between(Date, as.Date('2021-07-12'), as.Date('2021-07-14')), 'On', HOx),
-         HOx = if_else(Year == 2021 & 
+         HOx = if_else(Year == 2021 & Reservoir == 'FCR' &
                          between(Date, as.Date('2021-07-26'), as.Date('2021-09-06')), 'On', HOx),
-         HOx = if_else(Year == 2021 & 
+         HOx = if_else(Year == 2021 & Reservoir == 'FCR' &
                          between(Date, as.Date('2021-09-14'), as.Date('2021-12-06')), 'On', HOx),
-         HOx = if_else(Year == 2022 & 
+         HOx = if_else(Year == 2022 & Reservoir == 'FCR' &
                          between(Date, as.Date('2022-03-22'), as.Date('2022-03-24')), 'On', HOx),
-         HOx = if_else(Year == 2022 & 
+         HOx = if_else(Year == 2022 & Reservoir == 'FCR' &
                          between(Date, as.Date('2022-03-29'), as.Date('2022-04-03')), 'On', HOx),
-         HOx = if_else(Year == 2022 & 
+         HOx = if_else(Year == 2022 & Reservoir == 'FCR' &
                          between(Date, as.Date('2022-03-22'), as.Date('2022-03-24')), 'On', HOx),
-         HOx = if_else(Year == 2022 & 
+         HOx = if_else(Year == 2022 & Reservoir == 'FCR' &
                          between(Date, as.Date('2022-05-19'), as.Date('2022-06-14')), 'On', HOx),
-         HOx = if_else(Year == 2022 & 
+         HOx = if_else(Year == 2022 & Reservoir == 'FCR' &
                          between(Date, as.Date('2022-06-21'), as.Date('2022-08-26')), 'On', HOx),
-         HOx = if_else(Year == 2022 & 
+         HOx = if_else(Year == 2022 & Reservoir == 'FCR' &
                          between(Date, as.Date('2022-08-29'), as.Date('2022-10-01')), 'On', HOx),
-         HOx = if_else(Year == 2022 & 
+         HOx = if_else(Year == 2022 & Reservoir == 'FCR' &
                          between(Date, as.Date('2022-10-03'), as.Date('2022-12-12')), 'On', HOx),
-         HOx = if_else(Year == 2023 & 
+         HOx = if_else(Year == 2023 & Reservoir == 'FCR' &
                          between(Date, as.Date('2023-03-06'), as.Date('2023-12-04')), 'On', HOx)) %>% 
@@
 ```{r Save all figures to folder if desired, eval=FALSE}
+
 #Figure 6
+ggsave(DO_MaxMetal_plotFinal, file = 'DOps_MaxMetal.png', path = myFilePath,
+       height = 5, width = 8, units = 'in')
+#Figure 7
 ggsave(plot = ComboFluxPlot, filename = 'CumulHypFlux_tTest_2018-2023.png', path = myFilePath, height = 4, width = 8, units = 'in')
-#Figure 7
+#Figure 8
 ggsave(plot = HypCumulFluxPlot, filename = 'CumulHypFlux_HOxBoxes_2018-2023.png', path = myFilePath, height = 4, width = 8, units = 'in')
-#Figure 8
-ggsave(ThreshPlotFinal, file = 'HOxTimingFeMn.png', path = myFilePath, height = 8, width = 8, units = 'in')
 #Figure 9
@@
 #Figure S4
-ggsave(DO_CumulMetal_plotFinal, file = 'DOps_SeasonalFlux.png', path = myFilePath,
-       height = 4, width = 8, units = 'in')
+ggsave(DO_CumulMetal_plotFinal, file = 'DOps_MaxMetal.png', path = myFilePath,
+       height = 5, width = 8, units = 'in')
 ```

### 2025-05-06 Manuscript1_figures.Rmd
Changing "pre" vs "post" TO categorization to better reflect overlapping 2018 FCR and BVR sampling periods. Updating Figure S3 and flux summary table.

@@
          TO = if_else(Reservoir == 'FCR' & Layer == 'Epilimnion' 
-                      & Date < as.Date('2018-09-03'), 'Pre_', TO),
+                      & Date < as.Date('2018-09-02'), 'Pre_', TO),
          TO = if_else(Reservoir == 'FCR' & Layer == 'Hypolimnion' 
-                      & Date < as.Date('2018-07-23'), 'Pre_', TO),
+                      & Date < as.Date('2018-07-22'), 'Pre_', TO),
          TO = if_else(Reservoir == 'FCR' & Layer == 'Epilimnion' 
-                      & between(Date, as.Date('2018-09-03'), as.Date('2018-10-21')), 'Pre', TO),
+                      & between(Date, as.Date('2018-09-02'), as.Date('2018-10-21')), 'Pre', TO),
          TO = if_else(Reservoir == 'FCR' & Layer == 'Hypolimnion' 
-                      & between(Date, as.Date('2018-07-23'), as.Date('2018-10-21')), 'Pre', TO),
-         TO = if_else(Year == 2018 & Reservoir == 'BVR' 
-                      & Date <= as.Date('2018-09-07'), 'Pre', TO),
+                      & between(Date, as.Date('2018-07-22'), as.Date('2018-10-21')), 'Pre', TO),
+         TO = if_else(Year == 2018 & Reservoir == 'BVR' & Layer == 'Epilimnion' 
+                      & between(Date, as.Date('2018-09-06'), as.Date('2018-10-21')), 'Pre', TO),
+         TO = if_else(Year == 2018 & Reservoir == 'BVR' & Layer == 'Hypolimnion' 
+                      & between(Date, as.Date('2018-08-01'), as.Date('2018-10-21')), 'Pre', TO),
          TO = if_else(Year == 2018 & Reservoir == 'FCR' 
@@
   mutate(Date = date(DateTime),
-         Year = year(DateTime)) %>% #HOx activated on 2018-04-23 @ noon
+         Year = year(DateTime)) %>%
   filter(Year == 2018| Year == 2019 | Year == 2020,
@@
            between(Date, as.Date('2019-05-18'), as.Date('2020-03-14'))|
-           Reservoir == 'BVR' & Depth_m == 10 & 
-           between(Date, as.Date('2020-05-16'), as.Date('2020-06-17'))|
            Reservoir == 'FCR' & Depth_m == 9 & Date < as.Date('2018-08-19')) %>% 
@@
   full_join(DO3) %>%
-  full_join(DO4) %>% 
   filter(Date <= as.Date('2023-12-31')) %>% 
-  mutate(Method = factor(Method, levels = c('edi.271.9', 'edi.725.5', 'edi.198.13'))) %>%
-  ungroup() %>% 
-  #add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2018-11-17'),
-  #        Year = 2018, Depth_m = as.factor(10), DO_mgL = NA, 
-  #        Method = as.factor('edi.198.13')) %>%
-  add_row(Reservoir = 'FCR', Site = 50, Date = as.Date('2018-08-19'),
-          Year = 2018, Depth_m = as.factor(9), DO_mgL = NA, 
-          Method = as.factor('edi.198.13')) %>%
-  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2018-12-05'),
-          Year = 2018, Depth_m = as.factor(10), DO_mgL = NA, 
-          Method = as.factor('edi.198.13')) %>%
-  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2019-05-17'),
-          Year = 2019, Depth_m = as.factor(10), DO_mgL = NA, 
-          Method = as.factor('edi.198.13')) %>%
-  #add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2019-10-18'),
-  #        Year = 2019, Depth_m = as.factor(10), DO_mgL = NA, 
-  #        Method = as.factor('edi.198.13')) %>%
+  ungroup() %>% #adding NAs to create appropriate line breaks
   add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-01-01'),
@@
           Method = as.factor('edi.725.5')) %>%
-  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-03-15'),
-          Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
-          Method = as.factor('edi.198.13')) %>% 
   add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-05-15'),
           Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
-          Method = as.factor('edi.198.13')) %>%
-  add_row(Reservoir = 'BVR', Site = 50, Date = as.Date('2020-06-05'),
-          Year = 2020, Depth_m = as.factor(10), DO_mgL = NA, 
-          Method = as.factor('edi.198.13')) %>%
-arrange(Date)
+          Method = as.factor('edi.198.13'))
 
@@
   theme_bw(base_size = 18) + theme(panel.grid = element_blank()) +
-  geom_line(aes(x = Date, y = DO_mgL, color = Reservoir, linetype = Method)) +
-  scale_linetype_manual(values = c('solid', 'solid', 'dotted')) + 
-  guides(linetype = guide_legend(title = 'Data Package')) +
+  geom_line(aes(x = Date, y = DO_mgL, color = Reservoir)) +
+  geom_point(aes(x = Date, y = DO_mgL, color = Reservoir), data = DO4, size = 0.5) +
   ylab('Dissolved Oxygen (mg/L)')
@@
   filter(TO == 'Pre') %>% 
-  group_by(Reservoir, Layer) %>% 
+  group_by(Reservoir, Layer, Year) %>% 
   summarise(MeanFeFlux = round(mean(AvgTFeFlux_gm2d, na.rm = T), digits = 3),
@@
 ggsave(DO_plot1, file = 'HypolimnionDO_2018_2023.png', path = myFilePath, height = 4, 
-       width = 6, units = 'in')
+       width = 8, units = 'in')
 #Figure S4

### 2025-05-06 StratStartScript.R
Adding script to determine when stratification occurs

@@ -1,0 +1,472 @@
+#Stratification Start Date Code
+
+rm(list=ls(all=TRUE))
+library(dplyr)
+library(tidyr)
+library(readxl)
+library(lubridate)
+library(readr)
+library(ggplot2)
+library(reshape2)
+library(scales)
+library(stringr)
+
+#Using Freya's functions
+
+
+#' get daily targets
+#' 
+#' @param infiles vector of EDI data files
+#' @param interpolate should interpolation be carried out
+#' @return a targets dataframe in VERA format
+
+get_targets <- function(infiles, interpolate = T, maxgap = 12) {
+  
+  
+  standard_names <- data.frame(variable_new = c('Temp_C','SpCond_uScm', 'Chla_ugL', 'fDOM_QSU'),
+                               variable = c('EXOTemp_C_1', 'EXOSpCond_uScm_1', 'EXOChla_ugL_1', 'EXOfDOM_QSU_1'))
+  targets <- NULL
+  
+  # Load data
+  message('Reading data from EDI...')
+  for (i in 1:length(infiles)) {
+    df <- read_csv(infiles[i], show_col_types = F, progress = F) |> 
+      filter(Site == 50) |> 
+      # mutate(site_id = ifelse(Reservoir == 'BVR', 'bvre', ifelse(Reservoir == 'FCR', 'fcre', Reservoir))) |> 
+      rename(datetime = DateTime,
+             site_id = Reservoir) |> 
+      filter(site_id %in% c('FCR', 'BVR')) |> 
+      select(-Site)
+    
+    df_flags <- df |> 
+      select(any_of(c('datetime', 'site_id')) | contains('Flag') & contains(standard_names$variable)) |> 
+      pivot_longer(cols = contains('Flag'),
+                   names_to = 'variable', 
+                   values_to = 'flag_value', 
+                   names_prefix = 'Flag_')
+    
+    df_observations <- df |> 
+      select(any_of(c('datetime', 'site_id')) | contains(standard_names$variable) & !contains('Flag')) |> 
+      pivot_longer(cols = -any_of(c('site_id', 'datetime')),
+                   names_to = 'variable', 
+                   values_to = 'observation', 
+                   names_prefix = 'Flag_')
+    
+    
+    # Filter any flagged data
+    message('Filtering flags...')
+    df_long <- inner_join(df_observations, df_flags, 
+                          # by = c('site_id', 'datetime', 'depth_m', 'variable'),
[…]

### 2025-05-07 Manuscript1_figures.Rmd
Removing relative file path and adding missing pacakge to p_load

@@
 ```{r Figure 8 script, eval=TRUE, include=FALSE}
-plot_vline <- read_csv('~/Documents/R Projects/Sed Traps/TO_Dates.csv') %>% 
+plot_vline <- read_csv('TO_Dates.csv') %>% 
   mutate(Date = as.Date(Date),

### 2025-08-27 Weather_com_figure_ABP.Rmd
Markdaown to make the met comparison figure

---
title: "Figure for Weather Comparison"
output: html_notebook
author: "Adrienne Breef-Pilz"
date: "2025-08-27"
---

This Markdown makes a figure comparing the average temperature, daily rain fall, and windspeed from Falling Creek Reservoir from 2018-2023. It uses data from EDI. The plot is for the SI of Cece Wood's Sed Trap manuscript.

```{r set up}
# load data packages
pacman::p_load(tidyverse)

```

```{r read in data}

# read in data from EDI and filter down to 2018-2023 and variables of temp, rainfall, and wind speed

# reading in the data package from 2024 to stay consistent with the other data products
met <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/389/8/d4c74bbb3b86ea293e5c52136347fbb0")

# filter down the data frame to the correct date and select the columns we need
met_2018_23 <- met|>
  filter(DateTime>=as.Date("2018-01-01") & DateTime< as.Date("2024-01-01"))|>
  select(DateTime, AirTemp_C_Average, Rain_Total_mm, WindSpeed_Average_m_s)|>
  mutate(Date = as.Date(DateTime))

```

```{r Daily average temp and wind speed}
# Get the daily average of temperature and wind speed

met_avg <- met_2018_23|>
  select(Date, AirTemp_C_Average, WindSpeed_Average_m_s)|>
  group_by(Date)|>
  summarise_at(vars(AirTemp_C_Average:WindSpeed_Average_m_s), mean, na.rm = TRUE)

```

```{r Daily sum of rain}
#Get the daily sum of rain fall and convert it from mm to cm

met_sum <- met_2018_23|>
  select(Date, Rain_Total_mm)|>
  group_by(Date)|>
  summarise(Rain_Total_sum_cm = sum(Rain_Total_mm)/10)

```

```{r merge}
# Merge the daily average data frame with the daily sum of rainfall data frame
met_all <- merge(met_avg, met_sum)

met_all <- met_all|>
  mutate(DOY = yday(Date),
         Year = year(Date),
         ddate = as.Date(DOY-1)) # make the DOY into a date but it is off by 1 so subtract and then convert it into a date format. This way they all have the same year and will stack on top of one another

# pivot the data frame longer to use facet_grid below
met_all_long <- met_all|>
  pivot_longer(!c(Date, DOY, Year, ddate), names_to = "variable", values_to = "obs")

```

```{r Figure}
# Make the figure and save it in the figures folder

# Rename the variable to fit in the labels
hum_names <- as_labeller(
     c(`Rain_Total_sum_cm` = "Daily Rain Toal cm", `AirTemp_C_Average` = "Daily Average Air Temp C",`WindSpeed_Average_m_s` = "Daily Averge Wind Speed m/s"))

# Make the plot here
ggplot(met_all_long, aes(x = ddate, y = obs, color = as.factor(Year)))+
  geom_point()+ # point or line?
  facet_grid(vars(variable), scales = "free", labeller = hum_names)+
  labs(color='Year') + 
  ylab("")+
  xlab("Date")+
  scale_x_date(date_breaks = "2 month", date_minor_breaks = "1 month",
             date_labels = "%B")+
  theme_bw(base_size = 15) #size of all the text in the figure.

 # can change dimensions as you see fit 
ggsave("figures/Met_com_2018_2023.png", width = 10, height = 8, dpi = 300, units = "in", device='png')
```

### 2025-08-28 Weather_com_figure_ABP.Rmd
Updated the script so each plot is seperate

@@
 ```{r Figure}
-# Make the figure and save it in the figures folder
+# Make the figures on one panel and save it in the figures folder
+# Just going to comment this out, but save it
 
-# Rename the variable to fit in the labels
-hum_names <- as_labeller(
-     c(`Rain_Total_sum_cm` = "Daily Rain Toal cm", `AirTemp_C_Average` = "Daily Average Air Temp C",`WindSpeed_Average_m_s` = "Daily Averge Wind Speed m/s"))
+# # Rename the variable to fit in the labels
+# hum_names <- as_labeller(
+#      c(`Rain_Total_sum_cm` = "Daily Rain Toal cm", `AirTemp_C_Average` = "Daily Average Air Temp C",`WindSpeed_Average_m_s` = "Daily Averge Wind Speed m/s"))
+# 
+# # Make the plot here
+# ggplot(met_all_long, aes(x = ddate, y = obs, color = as.factor(Year)))+
+#   geom_point()+ # point or line?
+#   facet_grid(vars(variable), scales = "free", labeller = hum_names)+
+#   labs(color='Year') + 
+#   ylab("")+
+#   xlab("Date")+
+#   scale_x_date(date_breaks = "2 month", date_minor_breaks = "1 month",
+#              date_labels = "%B")+
+#   theme_bw(base_size = 15) #size of all the text in the figure. 
+# 
+# 
+#  # can change dimensions as you see fit 
+# ggsave("figures/Met_com_2018_2023.png", width = 10, height = 8, dpi = 300, units = "in", device='png')
+```
+```{r Function to Make Plots}
 
-# Make the plot here
-ggplot(met_all_long, aes(x = ddate, y = obs, color = as.factor(Year)))+
-  geom_point()+ # point or line?
-  facet_grid(vars(variable), scales = "free", labeller = hum_names)+
+# Function to make the Plots
+
+met_plot <- function(data= met_all_long,
+                     VAR, 
+                     y_lab){
+
+a <- met_all_long%>%
+  filter(variable == VAR)%>%
+ggplot(., aes(x = ddate, y = obs, color = as.factor(Year)))+
+  geom_point()+ 
   labs(color='Year') +
-  ylab("")+
+  ylab(y_lab)+
   xlab("Date")+
@@
              date_labels = "%B")+
-  theme_bw(base_size = 15) #size of all the text in the figure.
+  theme_bw(base_size = 18) #size of all the text in the figure.
+
+return(a)
+}
+```
+
+```{r Temp Plot}
+temp <- met_plot(VAR = "AirTemp_C_Average", y_lab = expression(""* ~degree*C))
+temp
 
  # can change dimensions as you see fit
-ggsave("figures/Met_com_2018_2023.png", width = 10, height = 8, dpi = 300, units = "in", device='png')
+ggsave("figures/SI_Met_Comp/Temp_2018_2023.png", plot = temp,width = 10, height = 8, dpi = 300, units = "in", device='png')
+
 ```
+
+```{r Wind speed}
+
+wind <- met_plot(VAR = "WindSpeed_Average_m_s", y_lab = "m/s")
+wind
+
+ # can change dimensions as you see fit
+ggsave("figures/SI_Met_Comp/Wind_2018_2023.png", plot = wind, width = 10, height = 8, dpi = 300, units = "in", device='png')
+
+```
+```{r Rain}
+rain <- met_plot(VAR = "Rain_Total_sum_cm", y_lab = "centimeters")
+rain
+
+ # can change dimensions as you see fit
+ggsave("figures/SI_Met_Comp/Rain_2018_2023.png", plot = rain, width = 10, height = 8, dpi = 300, units = "in", device='png')
+
+```
+
+```{r Violin plots}
+# Playing with box plots
+
+Atemp <- met_2018_23%>%
+  mutate(Year = year(DateTime))%>%
+  ggplot(., aes(x = Year, y = AirTemp_C_Average, group = Year, fill = as.factor(Year)))+
+  geom_violin()+
+  theme_bw()
+
+Atemp
+
+Wspeed <- met_2018_23%>%
+  mutate(Year = year(DateTime))%>%
+  ggplot(., aes(x = Year, y = WindSpeed_Average_m_s, group = Year, fill = as.factor(Year)))+
+  geom_violin()+
+  theme_bw()
+
+Wspeed
+
+```

### 2025-09-02 Weather_com_figure_ABP.Rmd

@@
 ```
+
 ```{r Function to Make Plots}
@@
 ggplot(., aes(x = ddate, y = obs, color = as.factor(Year)))+
-  geom_point()+ 
+  geom_line()+ 
   labs(color='Year') +
   ylab(y_lab)+
-  xlab("Date")+
+  xlab("")+
   scale_x_date(date_breaks = "2 month", date_minor_breaks = "1 month",

### 2025-09-03 ABP_heatmap_for_Cece_20241018.Rmd
Removing relative file path and adding missing pacakge to p_load
Added YSI data to heatmaps

@@
 
-pacman::p_load(tidyverse, akima, reshape2, gridExtra, colorRamps, RColorBrewer, ggpubr, geomtextpath, scales)
+pacman::p_load(tidyverse, akima, reshape2, gridExtra, colorRamps, RColorBrewer, ggpubr, geomtextpath, scales, rLakeAnalyzer)
 
@@
    select(-starts_with("Flag"))%>%
-  mutate(Year=year(DateTime))%>%
+  mutate(Year=year(DateTime),
+         Date = date(DateTime))%>%
   filter(Depth_m>0)
@@
   select(Reservoir, DateTime, Year)|>
-  unique()
+  mutate(Date = date(DateTime)) %>% 
+  distinct(Reservoir, Date, .keep_all = TRUE)
 
@@
   CTD_casts$MDay <- as.Date(CTD_casts$MDay, "%m-%d")
+
+# Make a vector of sampling days so CTD and handhelds do not overlap
+  CTD_days <- EDI_CTD %>% 
+    select(Date) %>% 
+    unique()
+
+# add in handhelds to supplement data gaps
+  Handhelds  <- read_csv("https://pasta.lternet.edu/package/data/eml/edi/198/13/e50a50d062ee73f4d85e4f20b360ce4f") %>% 
+    filter(between(DateTime, as.Date('2018-01-01 00:00:00'),
+                   as.Date('2023-12-31 23:59:59')),
+           Reservoir == 'FCR' | Reservoir == 'BVR',
+           Site == 50,
+           Depth_m >= 0) %>% 
+    arrange(DateTime)
+
+'%!in%' <- function(x,y)!('%in%'(x,y))
+
+Handhelds1 <- Handhelds %>% 
+  mutate(Date = date(DateTime),
+         Year = year(DateTime)) %>% 
+  filter(Date %!in% CTD_days$Date) %>% 
+  select(Reservoir, Site, DateTime, Depth_m, Temp_C, DO_mgL, Date, Year) %>% 
+  #fixing leap day issue, shifting sample date by one day
+  mutate(Date = if_else(Date == as.Date('2020-02-29'), 
+                          as.Date('2020-02-28'), Date))
+
+# Make a df of just the casts
+
+Handheld_days <- Handhelds1 |>
+  select(Reservoir, Date, DateTime, Year)|>
+  distinct(Reservoir, Date, .keep_all = TRUE)
+
+# GEt the month and date for easier graphing. This is not the correct date.   
+  Handheld_days$MonthDay <- format(Handheld_days$Date,"%m-%d")
+  Handheld_days$MDay <- as.Date(Handheld_days$MonthDay, "%m-%d")
+
+EDI_CTD_Handhelds <- EDI_CTD %>% 
+  select(Reservoir, Site, DateTime, Depth_m, Temp_C, DO_mgL, Date, Year) %>% 
+  rbind(Handhelds1) %>% 
+  na.omit() %>% 
+  arrange(Date)
 
@@
                                         yo = seq(min(bvr$Depth_m), max(bvr$Depth_m), 
-                                                 by = 0.1), 
+                                                 by = 0.5), 
                                         duplicate = "mean"),data.frame = T)
@@
 
-```{r plotting}
+```{r heat map}
 
@@
     data,
-    sample_dates,
+    sample_dates1,
+    sample_dates2,
     turnovers,
@@
   geom_raster(aes(x=MDay, y=y,fill = z))+
-  geom_point(data = sample_dates, aes(x = MDay, y = 0.1, z = NULL), pch = '|', size = 2, color = "black") + #to mark cast dates 
+  geom_point(data = sample_dates1, aes(x = MDay, y = 0.1, z = NULL), pch = '|', size = 2, color = "black") + #to mark cast dates 
+  geom_point(data = sample_dates2, aes(x = MDay, y = 0.1, z = NULL), pch = '|', size = 2, color = "black") +
    geom_vline(data= turnovers, aes(xintercept=MDay) , linetype="solid", color="black", linewidth=0.5) +
@@
 wer <- data.frame(
-  data= c(rep("EDI_CTD",12)),
+  data= c(rep("EDI_CTD_Handhelds",12)),
   var = c(rep("Temp_C",12)),
@@
   data= temp_df,
-  sample_dates = CTD_casts,
+  sample_dates1 = CTD_casts,
+  sample_dates2 = Handheld_days,
   turnovers = turnover, 
@@
   y_units = "Water temperature (°C)",
-  output_file = "figures/SedTraps_CTD_waterTemp_2018_2023.jpeg"
+  output_file = "figures/SedTraps_waterTemp_2018_2023.jpeg"
 )
@@
 wer <- data.frame(
-  data= c(rep("EDI_CTD",12)),
+  data= c(rep("EDI_CTD_Handhelds",12)),
   var = c(rep("DO_mgL",12)),
@@
   y_units = "Dissolved Oxygen mg/L",
-  output_file = "figures/SedTraps_CTD_DO_2018_2023.jpeg"
+  output_file = "figures/SedTraps_DO_2018_2023.jpeg"
 )

### 2025-09-10 ABP_heatmap_for_Cece_20241018.Rmd
Adding pH heat map

@@
   geom_point(data = sample_dates1, aes(x = MDay, y = 0.1, z = NULL), pch = '|', size = 2, color = "black") + #to mark cast dates 
-  geom_point(data = sample_dates2, aes(x = MDay, y = 0.1, z = NULL), pch = '|', size = 2, color = "black") +
+  geom_point(data = sample_dates2, aes(x = MDay, y = 0.1, z = NULL), pch = '|', size = 2, color = "red") +
    geom_vline(data= turnovers, aes(xintercept=MDay) , linetype="solid", color="black", linewidth=0.5) +
@@
   output_file = "figures/SedTraps_DO_2018_2023.jpeg"
+)
+
+```
+
+```{r pH set up}
+CTD_pH <- EDI_CTD %>% 
+  select(Reservoir, Site, DateTime, Depth_m, pH, Date, Year) %>% 
+  na.omit()
+
+CTD_pH_casts <- CTD_pH |>
+  select(Reservoir, DateTime, Year)|>
+  mutate(Date = date(DateTime)) %>% 
+  distinct(Reservoir, Date, .keep_all = TRUE)
+
+# GEt the month and date for easier graphing. This is not the correct date.   
+  CTD_pH_casts$MDay <- format(CTD_pH_casts$DateTime,"%m-%d")
+  CTD_pH_casts$MDay <- as.Date(CTD_pH_casts$MDay, "%m-%d")
+
+# Make a vector of sampling days so CTD and handhelds do not overlap
+  CTD_pH_days <- CTD_pH %>% 
+    select(Date) %>% 
+    unique()
+
+pH_Handhelds <- Handhelds %>% 
+  mutate(Date = date(DateTime),
+         Year = year(DateTime)) %>%
+  select(Reservoir, Site, DateTime, Depth_m, pH, Date, Year) %>%
+  na.omit() %>% 
+  filter(Date %!in% CTD_pH_days$Date) %>% 
+  #fixing leap day issue, shifting sample date by one day
+  mutate(Date = if_else(Date == as.Date('2020-02-29'), 
+                          as.Date('2020-02-28'), Date))
+
+CTD_Handhelds_pH <- CTD_pH %>% 
+  rbind(pH_Handhelds) %>% 
+  na.omit() %>% 
+  arrange(Date)
+
+Handheld_pH_days <- pH_Handhelds |>
+  select(Reservoir, Date, DateTime, Year)|>
+  distinct(Reservoir, Date, .keep_all = TRUE)
+
+# GEt the month and date for easier graphing. This is not the correct date.   
+  Handheld_pH_days$MonthDay <- format(Handheld_pH_days$Date,"%m-%d")
+  Handheld_pH_days$MDay <- as.Date(Handheld_pH_days$MonthDay, "%m-%d")
+```
+
+```{r pH heat map}
+
+#custom_heatmap_palettes <- c("#313695", "#4575b4", "#74add1",
+#                            "#abd9e9", "#e0f3f8", "#ffffbf", 
+#                            "#fee090","#fdae61", "#f46d43", 
+#                            "#d73027", "#a50026")
+
+make_pH_heat_map <- function(
+    data,
+    sample_dates1,
+    sample_dates2,
+    turnovers,
+    y_lim,
+    custom_heatmap_palette,
+    y_units,
+    output_file){
+
+#Heatmap
+
+# change the plots dimensions  
+jpeg(paste0(output_file),width = 8, height = 4, units = "in", res = 400)
+water_temp <- data%>%
+  mutate(x = as.Date(x, origin = "1970-01-01"),
+         Year = year(x))%>%
+  filter(!is.na(z))%>%
+  ggplot()+
+  geom_raster(aes(x=MDay, y=y,fill = z))+
+  geom_point(data = sample_dates1, aes(x = MDay, y = 0.1, z = NULL), pch = '|', size = 2, color = "black") + #to mark cast dates 
+  geom_point(data = sample_dates2, aes(x = MDay, y = 0.1, z = NULL), pch = '|', size = 2, color = "black") +
+   geom_vline(data= turnovers, aes(xintercept=MDay) , linetype="solid", color="black", linewidth=0.5) +
+  labs(y = "Depth (m)") +
+  scale_x_date(expand = c(0,0)) +
+  scale_y_reverse(expand = c(0,0)) +
+  #scale_y_continuous(expand = c(0,0))+
+  theme(panel.border = element_rect(fill = NA),
+        axis.title.x=element_blank())+
+  scale_fill_gradientn(name = y_units,
+                       limits = y_lim,
+                       colours = custom_heatmap_palette)+
+  facet_grid(rows= vars(Reservoir),cols = vars(Year),
+             scales = "free_y",
+             space = "free"
+             )+
+  theme(panel.background = element_rect(fill = "white"),
+          panel.spacing.x = unit(0.05, "lines"),
+        legend.position = 'bottom',
+        panel.grid = element_blank())
+  theme_bw(base_size = 18)
+  # labs(color = "")+
+  # geom_point(data = sensor_depth_plot, 
+  #            aes(x = Date, y = Sensor_depth), 
+  #            shape = 23, fill = "black", color = "white", size  =2.5)+
+  # geom_vline(data=lines,aes(xintercept = Dates), show.legend = F)+
+  # scale_linetype_manual(values = c("solid","84"),
+  #                       limits = c("Thermocline","Outtake pipe"),  
+  #                       name= NULL)+
+
+print(water_temp)
+dev.off()
+
+}
+```
+
+```{r Make pH plot}
+
+# EDI_CTD_temp <- EDI_CTD|>
+#   select(Reservoir, DateTime, Year, Depth_m, Temp_C)
+
+wer <- data.frame(
+  data= c(rep("CTD_Handhelds_pH",12)),
+  var = c(rep("pH",12)),
+  Res = c(rep("FCR",6), rep("BVR",6)),
+  Years = c(rep(2018:2023,2))
+)
+
+system.time(sd <- wer%>%
+             pmap(heat_interp))
+
+#Bind all the QAQC files from above
+   temp_df <- dplyr::bind_rows(sd)
+
+  temp_df <- temp_df%>%
+    filter(!is.na(Reservoir),
+           y>0.1) %>% 
+    na.omit()
+
+# GEt the month and date for easier graphing. This is not the correct date.   
+temp_df$MDay <- format(temp_df$Date,"%m-%d")
+temp_df$MDay <- as.Date(temp_df$MDay, "%m-%d")
+
+# make the plot
+
+make_pH_heat_map(
+  data= temp_df,
+  sample_dates1 = CTD_pH_casts,
+  sample_dates2 = Handheld_pH_days,
+  turnovers = turnover, 
+  y_lim = c(5.5, 10.5),
+  custom_heatmap_palette = rev(blue2green2red(60)),
+  y_units = "pH",
+  output_file = "figures/SedTraps_pH_2018_2023.jpeg"
 )

### 2025-09-10 ABP_heatmap_for_Cece_20241018.Rmd
Fixing geom_point color

@@
   geom_point(data = sample_dates1, aes(x = MDay, y = 0.1, z = NULL), pch = '|', size = 2, color = "black") + #to mark cast dates 
-  geom_point(data = sample_dates2, aes(x = MDay, y = 0.1, z = NULL), pch = '|', size = 2, color = "red") +
+  geom_point(data = sample_dates2, aes(x = MDay, y = 0.1, z = NULL), pch = '|', size = 2, color = "black") +
    geom_vline(data= turnovers, aes(xintercept=MDay) , linetype="solid", color="black", linewidth=0.5) +

### 2025-09-10 Manuscript1_figures.Rmd
Created extra DO plot to show how HOx increases DO

@@
 
+DOF4 <- DO4 %>% 
+  filter(Reservoir == 'FCR')
+
 DO <- DO1 %>% 
@@
 ```
+
+```{r}
+DO_plot2 <- DO %>%
+  filter(Reservoir == 'FCR') %>% 
+  ggplot() + theme_bw() + theme(panel.grid = element_blank()) + 
+  facet_grid(cols = vars(Year), scales = 'free') +
+  scale_x_date(date_labels = '%b', breaks = '3 months') +
+  geom_line(aes(x = Date, y = DO_mgL, color = Reservoir)) +
+  geom_point(aes(x = Date, y = DO_mgL, color = Reservoir),
+             data = DOF4, size = 0.5) +
+  geom_rect(aes(xmin = HOxOn, xmax = HOxOff, group = Group), ymin = -Inf, ymax = Inf, data = HOxBoxes, alpha = 0.2) +
+  ylab('Dissolved Oxygen (mg/L)')
+
+```

### 2025-09-10 ABP_heatmap_for_Cece_20241018.Rmd
Added turbidity heatmap

@@
 
+```{r turbidity set up}
+CTD_turb <- EDI_CTD %>% 
+  select(Reservoir, Site, DateTime, Depth_m, Turbidity_NTU, Date, Year) %>% 
+  na.omit() %>% 
+  filter(Turbidity_NTU <= 100)
+
+CTD_turb_casts <- CTD_turb |>
+  select(Reservoir, DateTime, Year)|>
+  mutate(Date = date(DateTime)) %>% 
+  distinct(Reservoir, Date, .keep_all = TRUE)
+
+# GEt the month and date for easier graphing. This is not the correct date.   
+  CTD_turb_casts$MDay <- format(CTD_turb_casts$DateTime,"%m-%d")
+  CTD_turb_casts$MDay <- as.Date(CTD_turb_casts$MDay, "%m-%d")
+```
+
+```{r turbidity heat map}
+
+#custom_heatmap_palettes <- c("#313695", "#4575b4", "#74add1",
+#                            "#abd9e9", "#e0f3f8", "#ffffbf", 
+#                            "#fee090","#fdae61", "#f46d43", 
+#                            "#d73027", "#a50026")
+
+make_turb_heat_map <- function(
+    data,
+    sample_dates1,
+    turnovers,
+    y_lim,
+    custom_heatmap_palette,
+    y_units,
+    output_file){
+
+#Heatmap
+
+# change the plots dimensions  
+jpeg(paste0(output_file),width = 8, height = 4, units = "in", res = 400)
+water_temp <- data%>%
+  mutate(x = as.Date(x, origin = "1970-01-01"),
+         Year = year(x))%>%
+  filter(!is.na(z))%>%
+  ggplot()+
+  geom_raster(aes(x=MDay, y=y,fill = z))+
+  geom_point(data = sample_dates1, aes(x = MDay, y = 0.1, z = NULL), pch = '|', size = 2, color = "black") + #to mark cast dates 
+   geom_vline(data= turnovers, aes(xintercept=MDay) , linetype="solid", color="black", linewidth=0.5) +
+  labs(y = "Depth (m)") +
+  scale_x_date(expand = c(0,0)) +
+  scale_y_reverse(expand = c(0,0)) +
+  #scale_y_continuous(expand = c(0,0))+
+  theme(panel.border = element_rect(fill = NA),
+        axis.title.x=element_blank())+
+  scale_fill_gradientn(name = y_units,
+                       limits = y_lim,
+                       colours = custom_heatmap_palette,
+                       values=rescale(c(0,20,100)))+
+  facet_grid(rows= vars(Reservoir),cols = vars(Year),
+             scales = "free_y",
+             space = "free"
+             )+
+  theme(panel.background = element_rect(fill = "white"),
+          panel.spacing.x = unit(0.05, "lines"),
+        legend.position = 'bottom',
+        panel.grid = element_blank())
+  theme_bw(base_size = 18)
+  # labs(color = "")+
+  # geom_point(data = sensor_depth_plot, 
+  #            aes(x = Date, y = Sensor_depth), 
+  #            shape = 23, fill = "black", color = "white", size  =2.5)+
+  # geom_vline(data=lines,aes(xintercept = Dates), show.legend = F)+
+  # scale_linetype_manual(values = c("solid","84"),
+  #                       limits = c("Thermocline","Outtake pipe"),  
+  #                       name= NULL)+
+
+print(water_temp)
+dev.off()
+
+}
+```
+
+```{r Make turbidity plot}
+
+# EDI_CTD_temp <- EDI_CTD|>
+#   select(Reservoir, DateTime, Year, Depth_m, Temp_C)
+
+wer <- data.frame(
+  data= c(rep("CTD_turb",12)),
+  var = c(rep("Turbidity_NTU",12)),
+  Res = c(rep("FCR",6), rep("BVR",6)),
+  Years = c(rep(2018:2023,2))
+)
+
+system.time(sd <- wer%>%
+             pmap(heat_interp))
+
+#Bind all the QAQC files from above
+   temp_df <- dplyr::bind_rows(sd)
+
+  temp_df <- temp_df%>%
+    filter(!is.na(Reservoir),
+           y>0.1) %>% 
+    na.omit()
+
+# GEt the month and date for easier graphing. This is not the correct date.   
+temp_df$MDay <- format(temp_df$Date,"%m-%d")
+temp_df$MDay <- as.Date(temp_df$MDay, "%m-%d")
+
+# make the plot
+
+make_turb_heat_map(
+  data= temp_df,
+  sample_dates1 = CTD_turb_casts,
+  turnovers = turnover, 
+  y_lim = c(0, 100),
+  custom_heatmap_palette = blue2green2red(60),
+  y_units = "Turbidity (NTU)",
+  output_file = "figures/SedTraps_turbidity_2018_2023.jpeg"
+)
+
+```
+
 ```{r metals plotting script}

### 2025-09-10 StratificationDifs_ASL.R
Cleaning up figure labels

@@ -492,9 +492,9 @@ fcre_temp_profile %>%
   geom_point()+
   geom_vline(aes(xintercept = start, color = site_id, lty = "Onset"), data = strat_dates)+
   geom_vline(aes(xintercept = end, color = site_id, lty = "Turnover"), data = strat_dates)+
-  ylab("Maximum buoyancy frequency (1/s)")+
+  ylab("Maximum Buoyancy Frequency (1/s)")+
   scale_linetype_discrete(name = "Stratification")+
-  facet_wrap(~site_id, ncol = 1)+
+  facet_wrap(~site_id, ncol = 1)+ labs(color = 'Site') +
   theme_bw()+
   theme(axis.title.x = element_blank())
 dev.off()
@@ -514,8 +514,8 @@ fcre_temp_profile %>%
   geom_abline()+
   geom_smooth(method = "lm")+
   theme_bw()+
-  xlab("FCR buoyancy frequency (1/s)")+
-  ylab("BVR buoyancy frequency (1/s)")
+  xlab("FCR Buoyancy Frequency (1/s)")+
+  ylab("BVR Buoyancy Frequency (1/s)")
 dev.off()
 
 strat_dates %>%
